
---
title: "Data_analysis"
output: html_notebook
editor_options: 
  chunk_output_type: console
chunk_output_type: console
---
Landscape ITS2 data for ICB symybiont sample paper

#Analysis
```{r} 
library(janitor)
library(phyloseq)  # source('http://bioconductor.org/biocLite.R'); biocLite('phyloseq')
library(zoo)
library(stringr)
library(vegan)
library(multcompView)
library("ggpubr")
library(ggplot2)
library(vegan)
library(pairwiseAdonis)
library(ecodist)
library(tidyverse)
 
load("data/DIV_abs_2025.RData") #absolute reads data
```

#Data Wrangle
#Remove low samples from the datasets (less than 2000)
Subsample to 750 (previously did 2k but this should be ok?)
```{r}
#DIVs
#Remove all samples with <750 reads and create sample data
DIVs.prune <- prune_samples(sample_sums(DIVs)>=750, DIVs) 
DIVs.prune_nonrare_sd <- as(sample_data(DIVs.prune), "data.frame")

#subsample to 750 reads
coral_DIV_750 <- rarefy_even_depth(DIVs.prune, sample.size = 750, rngseed = 711)    
sample_sums(coral_DIV_750) 
coral_DIV_750.sd <- as(sample_data(coral_DIV_750), "data.frame")
```

Turn subsampled df in to relative abundance: 
```{r}
#DIVs
DIV_RelA  = transform_sample_counts(coral_DIV_750, function(x) x / sum(x) )  #save as RELA DIVs
data.ra <- as(sample_data(DIV_RelA), "data.frame") #
 DIV_RelA = prune_taxa(taxa_sums(DIV_RelA) > 0, DIV_RelA) #this removes any OTU with 0s
```

# Make distance matrix -DIVs- for PERMANOVA
```{r}
#make bray curtis data matrix
  bc <- phyloseq::distance(DIV_RelA, method = "bray")

  data <- as(sample_data(DIV_RelA), "data.frame") #sample df
  data$Prop.D<-as.numeric(data$Prop.D)
  data$Prop.C<-as.numeric(data$Prop.C)
  data$Location<-as.factor(data$Location)
  data$TagID<-as.factor(data$TagID)
  data$Sample_name<-as.factor(data$Sample_name)
  data$dom<-as.factor(data$dom)

####Adonis2 - PERMANOVA (Ross- running into a strange error in the model output, turning up as "Model" not the main effect. "Margin" works but unsure if I trust it)

#PERMANOVA between colonies
 set.seed(30)
PERMANOVA <- vegan::adonis2(bc ~ TagID, data = data, by = "margin")
  PERMANOVA

  vegan::betadisper(bc, data$TagID) %>% anova()

# location nested, also weird Model output
PERMANOVA <- vegan::adonis2(bc ~ TagID / Location, data = data,by = "margin")
PERMANOVA

# location nested, also weird Model output
PERMANOVA <- vegan::adonis2(bc ~ TagID / dom, data = data,by = "margin")
PERMANOVA
```
Figures - PCOA

```{r} 
### plot by Proportion D ##############3
 #Color points by proportion of D using PCOA
bray_pcoa <- ecodist::pco(bc)
bray_pcoa_df <- data.frame(pcoa1 = bray_pcoa$vectors[,1],
                           pcoa2 = bray_pcoa$vectors[,2])
head(bray_pcoa_df)
bray_pcoa_df$Prop.D <- data$Prop.D
bray_pcoa_df$Prop.D<-as.numeric(bray_pcoa_df$Prop.D)
bray_pcoa_df$TagID <-data$TagID
bray_pcoa_df$Location <-data$Location

#color by Prop.D
pcoa <- ggplot(bray_pcoa_df, aes(x=pcoa1, y=pcoa2, color = Prop.D)) + 
  geom_point(size = 3,show.legend = T) +
  labs(x = "PC1",
       y = "PC2",
       title = "PCoA of ITS2 vs PropD") +
  theme_bw();pcoa
  pcoa+facet_wrap(~TagID)

#plot color by genotype and location  
library(qualpalr) #generate diverging colors
pal = qualpal(24, colorspace=list(h=c(10,350), s=c(0.3,1), l=c(0.2,0.8)))

  pcoa <- ggplot(bray_pcoa_df, aes(x=pcoa1, y=pcoa2, color = TagID)) + 
  geom_point(size = 3,show.legend = F) +
    scale_color_manual(values=pal$hex)+
  labs(x = "PC1",
       y = "PC2",
       title = "PCoA of ITS2 vs PropD") +
  theme_bw();pcoa
  pcoa+facet_wrap(~TagID)
```  
  
#Adonis within colony:
Subset by colony DIV, data setup
```{r} 
sample_variables(DIVs) #what are the variables

#970
Mcap_970 <- subset_samples(DIV_RelA, TagID =="970") #Subset by colony 
  Mcap_970.dist <- phyloseq::distance(Mcap_970, method = "bray")
  samp.Mcap_970<- as(sample_data(Mcap_970), "data.frame") #sample df
  
    #adonis by colony level
    adonis2(Mcap_970.dist ~ Sample_name, data = samp.Mcap_970, by = "margin")

    #anova
     aov.propD = aov(Prop.D ~Sample_name, data=samp.Mcap_970)
      summary(aov.propD)
      TukeyHSD(aov.propD)
    
#965
Mcap_965 <- subset_samples(DIV_RelA, TagID =="965") #Subset by colony  
  Mcap_965.dist <- phyloseq::distance(Mcap_965, method = "bray")
  samp.Mcap_965<- as(sample_data(Mcap_965), "data.frame") #sample df
  
    #adonis by colony level
    adonis2(Mcap_965.dist ~ Sample_name, data = samp.Mcap_965,by = "margin")

    #no anova, no D
    
#969
Mcap_969 <- subset_samples(DIV_RelA, TagID =="969") #Subset by colony  
  Mcap_969.dist <- phyloseq::distance(Mcap_969, method = "bray")
  samp.Mcap_969<- as(sample_data(Mcap_969), "data.frame") #sample df
  
    #adonis by colony level
    adonis2(Mcap_969.dist ~ Sample_name, data = samp.Mcap_969, by = "margin")
    
    #anova
     aov.propD = aov(Prop.D ~Location, data=samp.Mcap_969)
      summary(aov.propD) 

#972
Mcap_972 <- subset_samples(DIV_RelA, TagID =="972") #Subset by colony  
  Mcap_972.dist <- phyloseq::distance(Mcap_972, method = "bray")
  samp.Mcap_972<- as(sample_data(Mcap_972), "data.frame") #sample df
  
    #adonis by colony level
      adonis2(Mcap_972.dist ~ Location, data = samp.Mcap_972,by = "margin")
    adonis2(Mcap_972.dist ~ Sample_name, data = samp.Mcap_972,by = "margin")
    
      #anova
     aov.propD = aov(Prop.D ~Sample_name, data=samp.Mcap_972)
      summary(aov.propD)
      TukeyHSD(aov.propD)  
   
#971
Mcap_971 <- subset_samples(DIV_RelA, TagID =="971") #Subset by colony  
  Mcap_971.dist <- phyloseq::distance(Mcap_971, method = "bray")
  samp.Mcap_971<- as(sample_data(Mcap_971), "data.frame") #sample df
  
    #adonis by colony level
    adonis2(Mcap_971.dist ~ Location, data = samp.Mcap_971)    
    adonis2(Mcap_971.dist ~ Sample_name, data = samp.Mcap_971)    

        #anova
     aov.propD = aov(Prop.D ~Location, data=samp.Mcap_971)
      summary(aov.propD)
      TukeyHSD(aov.propD)
    
#968
Mcap_968 <- subset_samples(DIV_RelA, TagID =="968") #Subset by colony  
  Mcap_968.dist <- phyloseq::distance(Mcap_968, method = "bray")
  samp.Mcap_968<- as(sample_data(Mcap_968), "data.frame") #sample df
  
    #adonis by colony level
    adonis2(Mcap_968.dist ~ Location, data = samp.Mcap_968)    
        adonis2(Mcap_968.dist ~ Sample_name, data = samp.Mcap_968)    

        #anova
     aov.propD = aov(Prop.D ~Location, data=samp.Mcap_968)
      summary(aov.propD)
      TukeyHSD(aov.propD)
    
#966
Mcap_966 <- subset_samples(DIV_RelA, TagID =="966") #Subset by colony  
  Mcap_966.dist <- phyloseq::distance(Mcap_966, method = "bray")
  samp.Mcap_966<- as(sample_data(Mcap_966), "data.frame") #sample df
  
    #adonis by colony level
    adonis2(Mcap_966.dist ~ Location, data = samp.Mcap_966)
        adonis2(Mcap_966.dist ~ Sample_name, data = samp.Mcap_966)

        #anova
     aov.propD = aov(Prop.D ~Location, data=samp.Mcap_966)
      summary(aov.propD)
      TukeyHSD(aov.propD)
      
      
#978
Mcap_978 <- subset_samples(DIV_RelA, TagID =="978") #Subset by colony  
  Mcap_978.dist <- phyloseq::distance(Mcap_978, method = "bray")
  samp.Mcap_978<- as(sample_data(Mcap_978), "data.frame") #sample df
  
    #adonis by colony level
    adonis2(Mcap_978.dist ~ Location, data = samp.Mcap_978)
        adonis2(Mcap_978.dist ~ Sample_name, data = samp.Mcap_978)

        #anova
     aov.propD = aov(Prop.D ~Location, data=samp.Mcap_978)
      summary(aov.propD)
      TukeyHSD(aov.propD)
      
 #963
Mcap_963 <- subset_samples(DIV_RelA, TagID =="963") #Subset by colony  
  Mcap_963.dist <- phyloseq::distance(Mcap_963, method = "bray")
  samp.Mcap_963<- as(sample_data(Mcap_963), "data.frame") #sample df
  
    #adonis by colony level
    adonis2(Mcap_963.dist ~ Location, data = samp.Mcap_963)
    adonis2(Mcap_963.dist ~ Sample_name, data = samp.Mcap_963)

        #anova
     aov.propD = aov(Prop.D ~Location, data=samp.Mcap_963)
      summary(aov.propD)
      TukeyHSD(aov.propD)
      
#961
Mcap_961 <- subset_samples(DIV_RelA, TagID =="961") #Subset by colony  
  Mcap_961.dist <- phyloseq::distance(Mcap_961, method = "bray")
  samp.Mcap_961<- as(sample_data(Mcap_961), "data.frame") #sample df
  
    #adonis by colony level
    adonis2(Mcap_961.dist ~ Location, data = samp.Mcap_961)
    
        #anova
     aov.propD = aov(Prop.D ~Location, data=samp.Mcap_970)
      summary(aov.propD)
      TukeyHSD(aov.propD)
      
#981
Mcap_981 <- subset_samples(DIV_RelA, TagID =="981") #Subset by colony  
  Mcap_981.dist <- phyloseq::distance(Mcap_981, method = "bray")
  samp.Mcap_981<- as(sample_data(Mcap_981), "data.frame") #sample df
  
    #adonis by colony level
    adonis2(Mcap_981.dist ~ Location, data = samp.Mcap_981)
    
        #anova
     aov.propD = aov(Prop.D ~Location, data=samp.Mcap_970)
      summary(aov.propD)
      TukeyHSD(aov.propD)
      
#967
Mcap_967 <- subset_samples(DIV_RelA, TagID =="967") #Subset by colony  
  Mcap_967.dist <- phyloseq::distance(Mcap_967, method = "bray")
  samp.Mcap_967<- as(sample_data(Mcap_967), "data.frame") #sample df
  
    #adonis by colony level
    adonis2(Mcap_967.dist ~ Location, data = samp.Mcap_967)
    
        #anova
     aov.propD = aov(Prop.D ~Location, data=samp.Mcap_970)
      summary(aov.propD)
      TukeyHSD(aov.propD)
      
#983
Mcap_983 <- subset_samples(DIV_RelA, TagID =="983") #Subset by colony  
  Mcap_983.dist <- phyloseq::distance(Mcap_983, method = "bray")
  samp.Mcap_983<- as(sample_data(Mcap_983), "data.frame") #sample df
  
    #adonis by colony level
    adonis2(Mcap_983.dist ~ Location, data = samp.Mcap_983)
    
        #anova
     aov.propD = aov(Prop.D ~Location, data=samp.Mcap_970)
      summary(aov.propD)
      TukeyHSD(aov.propD)
      
#974
Mcap_974 <- subset_samples(DIV_RelA, TagID =="974") #Subset by colony  
  Mcap_974.dist <- phyloseq::distance(Mcap_974, method = "bray")
  samp.Mcap_974<- as(sample_data(Mcap_974), "data.frame") #sample df
  
    #adonis by colony level
    adonis2(Mcap_974.dist ~ Location, data = samp.Mcap_974)
    
        #anova
     aov.propD = aov(Prop.D ~Location, data=samp.Mcap_970)
      summary(aov.propD)
      TukeyHSD(aov.propD)
      
#984
Mcap_984 <- subset_samples(DIV_RelA, TagID =="984") #Subset by colony  
  Mcap_984.dist <- phyloseq::distance(Mcap_984, method = "bray")
  samp.Mcap_984<- as(sample_data(Mcap_984), "data.frame") #sample df
  
    #adonis by colony level
    adonis2(Mcap_984.dist ~ Location, data = samp.Mcap_984)
    
        #anova
     aov.propD = aov(Prop.D ~Location, data=samp.Mcap_970)
      summary(aov.propD)
      TukeyHSD(aov.propD)
      
#962
Mcap_962 <- subset_samples(DIV_RelA, TagID =="962") #Subset by colony  
  Mcap_962.dist <- phyloseq::distance(Mcap_962, method = "bray")
  samp.Mcap_962<- as(sample_data(Mcap_962), "data.frame") #sample df
  
    #adonis by colony level
    adonis2(Mcap_962.dist ~ Location, data = samp.Mcap_962)
    
        #anova
     aov.propD = aov(Prop.D ~Location, data=samp.Mcap_970)
      summary(aov.propD)
      TukeyHSD(aov.propD)
      
#957
Mcap_957 <- subset_samples(DIV_RelA, TagID =="957") #Subset by colony  
  Mcap_957.dist <- phyloseq::distance(Mcap_957, method = "bray")
  samp.Mcap_957<- as(sample_data(Mcap_957), "data.frame") #sample df
  
    #adonis by colony level
    adonis2(Mcap_957.dist ~ Location, data = samp.Mcap_957)
    
        #anova
     aov.propD = aov(Prop.D ~Location, data=samp.Mcap_970)
      summary(aov.propD)
      TukeyHSD(aov.propD)
      
#945
Mcap_945 <- subset_samples(DIV_RelA, TagID =="945") #Subset by colony  
  Mcap_945.dist <- phyloseq::distance(Mcap_945, method = "bray")
  samp.Mcap_945<- as(sample_data(Mcap_945), "data.frame") #sample df
  
    #adonis by colony level
    adonis2(Mcap_945.dist ~ Location, data = samp.Mcap_945)
        
        #anova
     aov.propD = aov(Prop.D ~Location, data=samp.Mcap_970)
      summary(aov.propD)
      TukeyHSD(aov.propD)
      
#960
Mcap_960 <- subset_samples(DIV_RelA, TagID =="960") #Subset by colony  
  Mcap_960.dist <- phyloseq::distance(Mcap_960, method = "bray")
  samp.Mcap_960<- as(sample_data(Mcap_960), "data.frame") #sample df
  
    #adonis by colony level
    adonis2(Mcap_960.dist ~ Location, data = samp.Mcap_960)
    
        #anova
     aov.propD = aov(Prop.D ~Location, data=samp.Mcap_970)
      summary(aov.propD)
      TukeyHSD(aov.propD)
      
#976
Mcap_976 <- subset_samples(DIV_RelA, TagID =="976") #Subset by colony  
  Mcap_976.dist <- phyloseq::distance(Mcap_976, method = "bray")
  samp.Mcap_976<- as(sample_data(Mcap_976), "data.frame") #sample df
  
    #adonis by colony level
    adonis2(Mcap_976.dist ~ Location, data = samp.Mcap_976)
    
        #anova
     aov.propD = aov(Prop.D ~Location, data=samp.Mcap_970)
      summary(aov.propD)
      TukeyHSD(aov.propD)
      
#985
Mcap_985 <- subset_samples(DIV_RelA, TagID =="985") #Subset by colony  
  Mcap_985.dist <- phyloseq::distance(Mcap_985, method = "bray")
  samp.Mcap_985<- as(sample_data(Mcap_985), "data.frame") #sample df
  
    #adonis by colony level
    adonis2(Mcap_985.dist ~ Location, data = samp.Mcap_985)
    
        #anova
     aov.propD = aov(Prop.D ~Location, data=samp.Mcap_970)
      summary(aov.propD)
      TukeyHSD(aov.propD)
      
#964
Mcap_964 <- subset_samples(DIV_RelA, TagID =="964") #Subset by colony  
  Mcap_964.dist <- phyloseq::distance(Mcap_964, method = "bray")
  samp.Mcap_964<- as(sample_data(Mcap_964), "data.frame") #sample df
  
    #adonis by colony level
    adonis2(Mcap_964.dist ~ Location, data = samp.Mcap_964)
    
        #anova
     aov.propD = aov(Prop.D ~Location, data=samp.Mcap_970)
      summary(aov.propD)
      TukeyHSD(aov.propD)
      
#959
Mcap_959 <- subset_samples(DIV_RelA, TagID =="959") #Subset by colony  
  Mcap_959.dist <- phyloseq::distance(Mcap_959, method = "bray")
  samp.Mcap_959<- as(sample_data(Mcap_959), "data.frame") #sample df
  
    #adonis by colony level
    adonis2(Mcap_959.dist ~ Location, data = samp.Mcap_959)
    
        #anova
     aov.propD = aov(Prop.D ~Location, data=samp.Mcap_970)
      summary(aov.propD)
      TukeyHSD(aov.propD)
      
#980
Mcap_980 <- subset_samples(DIV_RelA, TagID =="980") #Subset by colony  
  Mcap_980.dist <- phyloseq::distance(Mcap_980, method = "bray")
  samp.Mcap_980<- as(sample_data(Mcap_980), "data.frame") #sample df
  
    #adonis by colony level
    adonis2(Mcap_980.dist ~ Location, data = samp.Mcap_980)
  
        #anova
     aov.propD = aov(Prop.D ~Location, data=samp.Mcap_970)
      summary(aov.propD)
      TukeyHSD(aov.propD)
```
Plots DIVS by colony
```{r}  

#for the legend
 plot_bar(Mcap_970,fill = "DIV")+
      geom_bar(aes(color=DIV, fill=DIV), stat="identity", position="stack")

Mcap_970_plot<-plot_bar(Mcap_970, "Sample_name", fill="DIV", title="Mcap_970")+
   theme(legend.position="none");Mcap_970_plot
Mcap_965_plot<-plot_bar(Mcap_965, "Sample_name", fill="DIV", title="Mcap_965")+
   theme(legend.position="none");Mcap_965_plot
Mcap_969_plot<-plot_bar(Mcap_969, "Sample_name", fill="DIV", title="Mcap_969")+
   theme(legend.position="none");Mcap_969_plot
Mcap_972_plot<-plot_bar(Mcap_972, "Sample_name", fill="DIV", title="Mcap_972")+
   theme(legend.position="none");Mcap_972_plot
Mcap_971_plot<-plot_bar(Mcap_971, "Sample_name", fill="DIV", title="Mcap_971")+
   theme(legend.position="none");Mcap_971_plot
Mcap_968_plot<-plot_bar(Mcap_968, "Sample_name", fill="DIV", title="Mcap_968")+
   theme(legend.position="none");Mcap_968_plot
Mcap_966_plot<-plot_bar(Mcap_966, "Sample_name", fill="DIV", title="Mcap_966")+
   theme(legend.position="none");Mcap_966_plot
Mcap_978_plot<-plot_bar(Mcap_978, "Sample_name", fill="DIV", title="Mcap_978")+
   theme(legend.position="none");Mcap_978_plot
Mcap_963_plot<-plot_bar(Mcap_963, "Sample_name", fill="DIV", title="Mcap_963")+
   theme(legend.position="none");Mcap_963_plot
Mcap_961_plot<-plot_bar(Mcap_961, "Sample_name", fill="DIV", title="Mcap_961")+
   theme(legend.position="none");Mcap_961_plot
Mcap_981_plot<-plot_bar(Mcap_981, "Sample_name", fill="DIV", title="Mcap_981")+
   theme(legend.position="none");Mcap_981_plot
Mcap_967_plot<-plot_bar(Mcap_967, "Sample_name", fill="DIV", title="Mcap_967")+
   theme(legend.position="none");Mcap_967_plot
Mcap_983_plot<-plot_bar(Mcap_983, "Sample_name", fill="DIV", title="Mcap_983")+
   theme(legend.position="none");Mcap_983_plot
Mcap_974_plot<-plot_bar(Mcap_974, "Sample_name", fill="DIV", title="Mcap_974")+
   theme(legend.position="none");Mcap_974_plot
Mcap_984_plot<-plot_bar(Mcap_984, "Sample_name", fill="DIV", title="Mcap_984")+
   theme(legend.position="none");Mcap_984_plot
Mcap_962_plot<-plot_bar(Mcap_962, "Sample_name", fill="DIV", title="Mcap_962")+
   theme(legend.position="none");Mcap_962_plot
Mcap_957_plot<-plot_bar(Mcap_957, "Sample_name", fill="DIV", title="Mcap_957")+
   theme(legend.position="none");Mcap_957_plot
Mcap_945_plot<-plot_bar(Mcap_945, "Sample_name", fill="DIV", title="Mcap_945")+
   theme(legend.position="none");Mcap_945_plot
Mcap_960_plot<-plot_bar(Mcap_960, "Sample_name", fill="DIV", title="Mcap_960")+
   theme(legend.position="none");Mcap_960_plot
Mcap_976_plot<-plot_bar(Mcap_976, "Sample_name", fill="DIV", title="Mcap_976")+
   theme(legend.position="none");Mcap_976_plot
Mcap_985_plot<-plot_bar(Mcap_985, "Sample_name", fill="DIV", title="Mcap_985")+
   theme(legend.position="none");Mcap_985_plot
Mcap_964_plot<-plot_bar(Mcap_964, "Sample_name", fill="DIV", title="Mcap_964")+
   theme(legend.position="none");Mcap_964_plot
Mcap_985_plot<-plot_bar(Mcap_985, "Sample_name", fill="DIV", title="Mcap_985")+
   theme(legend.position="none");Mcap_985_plot
Mcap_959_plot<-plot_bar(Mcap_959, "Sample_name", fill="DIV", title="Mcap_959")+
   theme(legend.position="none");Mcap_959_plot
Mcap_980_plot<-plot_bar(Mcap_980, "Sample_name", fill="DIV", title="Mcap_980")+
   theme(legend.position="none");Mcap_980_plot

#name of sample location on C/Ds
Mcap_970_plotB<-plot_bar(Mcap_970, "LocSamp", fill="DIV", title="Mcap_970")+
   theme(legend.position="none");Mcap_970_plotB


Mcap_DIV_plot1 <- ggarrange(Mcap_970_plot, Mcap_965_plot,Mcap_969_plot,Mcap_972_plot, Mcap_971_plot,Mcap_968_plot,Mcap_966_plot,Mcap_978_plot,
                    #labels = c("A", "B", "C","D","E","F"),
                    ncol = 4, nrow = 2);Mcap_DIV_plot1

Mcap_DIV_plot2 <- ggarrange(Mcap_963_plot, Mcap_961_plot,Mcap_981_plot,Mcap_967_plot,
Mcap_983_plot,Mcap_974_plot,Mcap_984_plot,Mcap_962_plot,
                    #labels = c("A", "B", "C","D","E","F"),
                    ncol = 4, nrow = 2);Mcap_DIV_plot2

Mcap_DIV_plot3 <- ggarrange(Mcap_957_plot,Mcap_945_plot,Mcap_960_plot,Mcap_976_plot,
Mcap_985_plot,Mcap_964_plot,Mcap_985_plot,Mcap_964_plot,Mcap_985_plot,Mcap_959_plot,Mcap_980_plot,
                    #labels = c("A", "B", "C","D","E","F"),
                    ncol = 4, nrow = 3);Mcap_DIV_plot3

```

Plots DIVS by colony
```{r}  

library(tidyr)
library(ggplot2)

# Convert wide data (Prop.C and Prop.D) to long format
df_long <- data %>%
  pivot_longer(cols = c("Prop.C", "Prop.D"), 
               names_to = "Clade", 
               values_to = "Proportion")

dom.colors <- c("Prop.C" = "deepskyblue", "Prop.D" = "orange")

# Create the plot
p<-ggplot(df_long, aes(x = SampleNum, y = Proportion, fill = Clade)) +
  geom_bar(stat = "identity", position = "stack") + 
  scale_fill_manual(values = dom.colors) +
  labs(x = "Tag ID", y = "Proportion", title = "Stacked Proportion of C and D in Each Tag.ID") +
  theme_minimal()
p+facet_wrap(~TagID)



```

#probability of 1 sample correctly identifying dom symbiont
```{r}

#I try this in 2 ways - 1. dom symbiont per colony by adding up all the rel abund data for 16 samples and seeing who is dom, and 2. getting dom symbiont per samp and using highest frequency of dom symb to assign dom symb per colony. 

#1. dom.colony = all 16 samples relative abundance. NOT by number of samples Dom C or D

prob<-data #make a copy
prob<-prob %>% 
  rename(
    dom.colony =   dom  )

prob<- transform(
  prob, Match= ifelse(dom.colony==dom.samp, "Y", "N"))

table(prob['Match']) # how many match or not. 
#359 Yes, 22 no

# Count mismatches per TagID
mismatch_counts <- prob %>%
  filter(Match == "N") %>%  # Only keep mismatches
  count(TagID, name = "Mismatch_Count")  # Count mismatches per TagID

# View results
print(mismatch_counts)


####2. this by most frequent dominant sample (add up Doms by sample and divide) This my make the most sense ####
# Compute dominant clade per TagID based on the most frequent `dom.samp`
dom_col_samp <- prob %>%
  group_by(TagID) %>%
  summarise(dom.col.samp = names(sort(table(dom.samp), decreasing = TRUE))[1])  # Get most common clade

# Merge back with original dataframe
prob <- left_join(prob, dom_col_samp, by = "TagID")

prob<- transform(
  prob, Match2= ifelse(dom.col.samp==dom.samp, "Y", "N"))

table(prob['Match2']) # how many match or not. 
#361 Yes, 20 no

# Count mismatches per TagID
mismatch_counts <- prob %>%
  filter(Match2 == "N") %>%  # Only keep mismatches
  count(TagID, name = "Mismatch_Count")  # Count mismatches per TagID

# View results - this might make more sense??
print(mismatch_counts)
```





