
---
title: "Data_analysis"
output: html_notebook
editor_options: 
  chunk_output_type: console
chunk_output_type: console
---
Landscape ITS2 data for ICB symybiont sample paper

#Analysis
```{r} 
library(janitor)
library(phyloseq)  # source('http://bioconductor.org/biocLite.R'); biocLite('phyloseq')
library(zoo)
library(stringr)
library(vegan)
library(multcompView)
library("ggpubr")
library(ggplot2)
library(vegan)
library(pairwiseAdonis)

library(tidyverse)
 
load("data/Absolute_2025.RData") #absolute reads data
```

#Data Wrangle
#Remove low samples from the datasets (less than 2000)
Subsample to 2000 reads ("NTC", "NTC2", "S6", "G7","Q11","G8", "B13","B6","C14)
```{r}
#DIVs
#Remove all samples with <750 reads and create sample data
coral_Absolute_DIV.prune <- prune_samples(sample_sums(coral_Absolute_DIV)>=750, coral_Absolute_DIV) 
coral_Absolute_DIV.prune_nonrare_sd <- as(sample_data(coral_Absolute_DIV.prune), "data.frame")

#subsample to 750 reads
coral_DIV_750 <- rarefy_even_depth(coral_Absolute_DIV.prune, sample.size = 750, rngseed = 711)    
sample_sums(coral_DIV_750) 
coral_DIV_750.sd <- as(sample_data(coral_DIV_750), "data.frame")


```

Turn subsampled df in to relative abundance: 
```{r}
#DIVs
DIV_RelA  = transform_sample_counts(coral_DIV_750, function(x) x / sum(x) )  #save as RELA DIVs
data.ra <- as(sample_data(DIV_RelA), "data.frame") #look at samp data
 DIV_RelA = prune_taxa(taxa_sums(DIV_RelA) > 0, DIV_RelA) #this removes any OTU with 0s
```

# Make distance matrix -DIVs
```{r}
#make bray curtis data matrix
  DIV_RelA.dist <- phyloseq::distance(DIV_RelA, method = "bray")

  samp.DIV_RelA.dist <- as(sample_data(DIV_RelA), "data.frame") #sample df
  samp.DIV_RelA.dist$Prop.D<-as.numeric(samp.DIV_RelA.dist$Prop.D)
  samp.DIV_RelA.dist$Prop.C<-as.numeric(samp.DIV_RelA.dist$Prop.C)
  samp.DIV_RelA.dist$Location<-as.factor(samp.DIV_RelA.dist$Location)
  samp.DIV_RelA.dist$LocSamp<-as.factor(samp.DIV_RelA.dist$LocSamp)
  samp.DIV_RelA.dist$TagID<-as.factor(samp.DIV_RelA.dist$TagID)
  samp.DIV_RelA.dist <- samp.DIV_RelA.dist[, -c(1:11,13:20,22:24, 26:27, 29:30)] #remove unneeded cols

```
Adonis2
```{r}

  #adonis by colony level or proportion D
library(vegan)
  set.seed(30)
  vegan::adonis2(DIV_RelA.dist ~ SampLoc, method ="bray",data = samp.DIV_RelA.dist) 

  
  sset.seed(30)
  adonis2(DIV_RelA.dist ~ Prop.D, data = samp.DIV_RelA.dist)
    
# Homogeneity of dispersion test
  betaTagID <- betadisper(DIV_RelA.dist, samp.DIV_RelA.dist$TagID)
  perm<-permutest(betaTagID, pairwise = T) 
  (betaTagID.HSD <- TukeyHSD(betaTagID)) #do you need? impossible to visualize
  plot(betaTagID.HSD)

#adonis by sample location and colony ID
  set.seed(30)
  adonis2(DIV_RelA.dist ~ Location*TagID, data = samp.DIV_RelA.dist)
    
     
# Homogeneity of dispersion test, Location
  betaTagID <- betadisper(DIV_RelA.dist, samp.DIV_RelA.dist$Location)
  perm<-permutest(betaTagID, pairwise = T)
  permutest(betadisper(DIV_RelA.dist, samp.DIV_RelA.dist$Location, type = "centroid")) #sig
  permutest(betadisper(DIV_RelA.dist, samp.DIV_RelA.dist$TagID, type = "centroid")) #sig
  permutest(betadisper(DIV_RelA.dist, samp.DIV_RelA.dist$Prop.D, type = "centroid")) #sig

  #adonis by broad location and colony ID
  set.seed(30)
  adonis2(DIV_RelA.dist ~ Location, data = samp.DIV_RelA.dist) #not significaant


#anova is location a predictor of propD <- does this work?
    aov.propD = aov(Prop.D ~ TagID*Location, data=samp.DIV_RelA.dist)
    summary(aov.propD) # only location sig
    
#plot
set.seed(30)
ord.DIV_RelA.dist<- ordinate(DIV_RelA, "NMDS", "bray", trymax = 100) 
stressplot(ord.DIV_RelA.dist)
scores.ord.DIV_RelA.dist <- as.data.frame(cbind(vegan::scores(ord.DIV_RelA.dist, display="sites"))) #make df
scores.ord.DIV_RelA.dist$TagID <- samp.DIV_RelA.dist$TagID
scores.ord.DIV_RelA.dist$col.branch <- samp.DIV_RelA.dist$col.branch
scores.ord.DIV_RelA.dist$Location <- samp.DIV_RelA.dist$Location
scores.ord.DIV_RelA.dist$Zoox <- samp.DIV_RelA.dist$Zoox

ggplot(scores.ord.DIV_RelA.dist, aes(x = NMDS1, y = NMDS2)) + 
  geom_point(aes(colour = TagID), size = 4,show.legend=T) +
  # scale_color_manual(values=Sp.colors)+
  # geom_text(label = rownames(Clade), nudge_x = 0.05, nudge_y = 0.05,check_overlap = T) +
  stat_ellipse(aes(x = NMDS1, y = NMDS2, colour = TagID), linetype = 2,show.legend=F) +
  ggtitle("NMDS its2 Bray Curtis TagID") +
  theme_classic()
  #facet_wrap(~Zoox)
#ggsave("NMDS_ITS2_allsamps.pdf")  
  
 ### plot by Proportion D ##############3

 #Color points by proportion of D
  library(ecodist)
bray_pcoa <- ecodist::pco(DIV_RelA.dist)
bray_pcoa_df <- data.frame(pcoa1 = bray_pcoa$vectors[,1],
                           pcoa2 = bray_pcoa$vectors[,2])
head(bray_pcoa_df)
bray_pcoa_df$Prop.D <- samp.DIV_RelA.dist$Prop.D
bray_pcoa_df$Prop.D<-as.numeric(bray_pcoa_df$Prop.D)
bray_pcoa_df$TagID <-samp.DIV_RelA.dist$TagID
bray_pcoa_df$Location <-samp.DIV_RelA.dist$Location

pcoa <- ggplot(bray_pcoa_df, aes(x=pcoa1, y=pcoa2, color = Prop.D)) + 
  geom_point(size = 3,show.legend = F) +
  labs(x = "PC1",
       y = "PC2",
       title = "PCoA of ITS2 vs PropD") +
  theme_bw();pcoa
  pcoa+facet_wrap(~TagID)

#plot color by genotype and location  
library(qualpalr) #generate diverging colors
pal = qualpal(24, colorspace=list(h=c(10,350), s=c(0.3,1), l=c(0.2,0.8)))

  pcoa <- ggplot(bray_pcoa_df, aes(x=pcoa1, y=pcoa2, color = TagID)) + 
  geom_point(size = 3,show.legend = F) +
    scale_color_manual(values=pal$hex)+
  labs(x = "PC1",
       y = "PC2",
       title = "PCoA of ITS2 vs PropD") +
  theme_bw();pcoa
  pcoa+facet_wrap(~TagID)

  #same by location (for slides)
  pcoa <- ggplot(bray_pcoa_df, aes(x=pcoa1, y=pcoa2, color = Location)) + 
  geom_point(size = 3,show.legend = T) +
  labs(x = "PC1",
       y = "PC2",
       title = "PCoA of ITS2 vs PropD") +
  theme_bw();pcoa
  pcoa+facet_wrap(~Location)
```  
  
#Adonis within colony:
Subset by colony DIV, data setup
```{r} 
sample_variables(DIV_RelA) #what are the variables

#970
Mcap_970 <- subset_samples(DIV_RelA, TagID =="970") #Subset by colony 
  Mcap_970.dist <- phyloseq::distance(Mcap_970, method = "bray")
  samp.Mcap_970<- as(sample_data(Mcap_970), "data.frame") #sample df
  
    #adonis by colony level
    adonis2(Mcap_970.dist ~ Location, data = samp.Mcap_970)

    #anova
     aov.propD = aov(Prop.D ~Location, data=samp.Mcap_970)
      summary(aov.propD)
      TukeyHSD(aov.propD)
    
#965
Mcap_965 <- subset_samples(DIV_RelA, TagID =="965") #Subset by colony  
  Mcap_965.dist <- phyloseq::distance(Mcap_965, method = "bray")
  samp.Mcap_965<- as(sample_data(Mcap_965), "data.frame") #sample df
  
    #adonis by colony level
    adonis2(Mcap_965.dist ~ Location, data = samp.Mcap_965)
    adonis2(Mcap_965.dist ~ SampLoc, data = samp.Mcap_965)

    #no anova, no D
    
#969
Mcap_969 <- subset_samples(DIV_RelA, TagID =="969") #Subset by colony  
  Mcap_969.dist <- phyloseq::distance(Mcap_969, method = "bray")
  samp.Mcap_969<- as(sample_data(Mcap_969), "data.frame") #sample df
  
    #adonis by colony level
    adonis2(Mcap_969.dist ~ Location, data = samp.Mcap_969)
    
    #anova
     aov.propD = aov(Prop.D ~Location, data=samp.Mcap_969)
      summary(aov.propD) 

#972
Mcap_972 <- subset_samples(DIV_RelA, TagID =="972") #Subset by colony  
  Mcap_972.dist <- phyloseq::distance(Mcap_972, method = "bray")
  samp.Mcap_972<- as(sample_data(Mcap_972), "data.frame") #sample df
  
    #adonis by colony level
    adonis2(Mcap_972.dist ~ Location, data = samp.Mcap_972)
    
      #anova
     aov.propD = aov(Prop.D ~Location, data=samp.Mcap_972)
      summary(aov.propD)
      TukeyHSD(aov.propD)  
   
#971
Mcap_971 <- subset_samples(DIV_RelA, TagID =="971") #Subset by colony  
  Mcap_971.dist <- phyloseq::distance(Mcap_971, method = "bray")
  samp.Mcap_971<- as(sample_data(Mcap_971), "data.frame") #sample df
  
    #adonis by colony level
    adonis2(Mcap_971.dist ~ Location, data = samp.Mcap_971)    

        #anova
     aov.propD = aov(Prop.D ~Location, data=samp.Mcap_971)
      summary(aov.propD)
      TukeyHSD(aov.propD)
    
#968
Mcap_968 <- subset_samples(DIV_RelA, TagID =="968") #Subset by colony  
  Mcap_968.dist <- phyloseq::distance(Mcap_968, method = "bray")
  samp.Mcap_968<- as(sample_data(Mcap_968), "data.frame") #sample df
  
    #adonis by colony level
    adonis2(Mcap_968.dist ~ Location, data = samp.Mcap_968)    
    
        #anova
     aov.propD = aov(Prop.D ~Location, data=samp.Mcap_968)
      summary(aov.propD)
      TukeyHSD(aov.propD)
    
#966
Mcap_966 <- subset_samples(DIV_RelA, TagID =="966") #Subset by colony  
  Mcap_966.dist <- phyloseq::distance(Mcap_966, method = "bray")
  samp.Mcap_966<- as(sample_data(Mcap_966), "data.frame") #sample df
  
    #adonis by colony level
    adonis2(Mcap_966.dist ~ Location, data = samp.Mcap_966)
    
        #anova
     aov.propD = aov(Prop.D ~Location, data=samp.Mcap_966)
      summary(aov.propD)
      TukeyHSD(aov.propD)
      
      
#978
Mcap_978 <- subset_samples(DIV_RelA, TagID =="978") #Subset by colony  
  Mcap_978.dist <- phyloseq::distance(Mcap_978, method = "bray")
  samp.Mcap_978<- as(sample_data(Mcap_978), "data.frame") #sample df
  
    #adonis by colony level
    adonis2(Mcap_978.dist ~ Location, data = samp.Mcap_978)
    
        #anova
     aov.propD = aov(Prop.D ~Location, data=samp.Mcap_978)
      summary(aov.propD)
      TukeyHSD(aov.propD)
      
 #963
Mcap_963 <- subset_samples(DIV_RelA, TagID =="963") #Subset by colony  
  Mcap_963.dist <- phyloseq::distance(Mcap_963, method = "bray")
  samp.Mcap_963<- as(sample_data(Mcap_963), "data.frame") #sample df
  
    #adonis by colony level
    adonis2(Mcap_963.dist ~ Location, data = samp.Mcap_963)

        #anova
     aov.propD = aov(Prop.D ~Location, data=samp.Mcap_963)
      summary(aov.propD)
      TukeyHSD(aov.propD)
      
#961
Mcap_961 <- subset_samples(DIV_RelA, TagID =="961") #Subset by colony  
  Mcap_961.dist <- phyloseq::distance(Mcap_961, method = "bray")
  samp.Mcap_961<- as(sample_data(Mcap_961), "data.frame") #sample df
  
    #adonis by colony level
    adonis2(Mcap_961.dist ~ Location, data = samp.Mcap_961)
    
        #anova
     aov.propD = aov(Prop.D ~Location, data=samp.Mcap_970)
      summary(aov.propD)
      TukeyHSD(aov.propD)
      
#981
Mcap_981 <- subset_samples(DIV_RelA, TagID =="981") #Subset by colony  
  Mcap_981.dist <- phyloseq::distance(Mcap_981, method = "bray")
  samp.Mcap_981<- as(sample_data(Mcap_981), "data.frame") #sample df
  
    #adonis by colony level
    adonis2(Mcap_981.dist ~ Location, data = samp.Mcap_981)
    
        #anova
     aov.propD = aov(Prop.D ~Location, data=samp.Mcap_970)
      summary(aov.propD)
      TukeyHSD(aov.propD)
      
#967
Mcap_967 <- subset_samples(DIV_RelA, TagID =="967") #Subset by colony  
  Mcap_967.dist <- phyloseq::distance(Mcap_967, method = "bray")
  samp.Mcap_967<- as(sample_data(Mcap_967), "data.frame") #sample df
  
    #adonis by colony level
    adonis2(Mcap_967.dist ~ Location, data = samp.Mcap_967)
    
        #anova
     aov.propD = aov(Prop.D ~Location, data=samp.Mcap_970)
      summary(aov.propD)
      TukeyHSD(aov.propD)
      
#983
Mcap_983 <- subset_samples(DIV_RelA, TagID =="983") #Subset by colony  
  Mcap_983.dist <- phyloseq::distance(Mcap_983, method = "bray")
  samp.Mcap_983<- as(sample_data(Mcap_983), "data.frame") #sample df
  
    #adonis by colony level
    adonis2(Mcap_983.dist ~ Location, data = samp.Mcap_983)
    
        #anova
     aov.propD = aov(Prop.D ~Location, data=samp.Mcap_970)
      summary(aov.propD)
      TukeyHSD(aov.propD)
      
#974
Mcap_974 <- subset_samples(DIV_RelA, TagID =="974") #Subset by colony  
  Mcap_974.dist <- phyloseq::distance(Mcap_974, method = "bray")
  samp.Mcap_974<- as(sample_data(Mcap_974), "data.frame") #sample df
  
    #adonis by colony level
    adonis2(Mcap_974.dist ~ Location, data = samp.Mcap_974)
    
        #anova
     aov.propD = aov(Prop.D ~Location, data=samp.Mcap_970)
      summary(aov.propD)
      TukeyHSD(aov.propD)
      
#984
Mcap_984 <- subset_samples(DIV_RelA, TagID =="984") #Subset by colony  
  Mcap_984.dist <- phyloseq::distance(Mcap_984, method = "bray")
  samp.Mcap_984<- as(sample_data(Mcap_984), "data.frame") #sample df
  
    #adonis by colony level
    adonis2(Mcap_984.dist ~ Location, data = samp.Mcap_984)
    
        #anova
     aov.propD = aov(Prop.D ~Location, data=samp.Mcap_970)
      summary(aov.propD)
      TukeyHSD(aov.propD)
      
#962
Mcap_962 <- subset_samples(DIV_RelA, TagID =="962") #Subset by colony  
  Mcap_962.dist <- phyloseq::distance(Mcap_962, method = "bray")
  samp.Mcap_962<- as(sample_data(Mcap_962), "data.frame") #sample df
  
    #adonis by colony level
    adonis2(Mcap_962.dist ~ Location, data = samp.Mcap_962)
    
        #anova
     aov.propD = aov(Prop.D ~Location, data=samp.Mcap_970)
      summary(aov.propD)
      TukeyHSD(aov.propD)
      
#957
Mcap_957 <- subset_samples(DIV_RelA, TagID =="957") #Subset by colony  
  Mcap_957.dist <- phyloseq::distance(Mcap_957, method = "bray")
  samp.Mcap_957<- as(sample_data(Mcap_957), "data.frame") #sample df
  
    #adonis by colony level
    adonis2(Mcap_957.dist ~ Location, data = samp.Mcap_957)
    
        #anova
     aov.propD = aov(Prop.D ~Location, data=samp.Mcap_970)
      summary(aov.propD)
      TukeyHSD(aov.propD)
      
#945
Mcap_945 <- subset_samples(DIV_RelA, TagID =="945") #Subset by colony  
  Mcap_945.dist <- phyloseq::distance(Mcap_945, method = "bray")
  samp.Mcap_945<- as(sample_data(Mcap_945), "data.frame") #sample df
  
    #adonis by colony level
    adonis2(Mcap_945.dist ~ Location, data = samp.Mcap_945)
        
        #anova
     aov.propD = aov(Prop.D ~Location, data=samp.Mcap_970)
      summary(aov.propD)
      TukeyHSD(aov.propD)
      
#960
Mcap_960 <- subset_samples(DIV_RelA, TagID =="960") #Subset by colony  
  Mcap_960.dist <- phyloseq::distance(Mcap_960, method = "bray")
  samp.Mcap_960<- as(sample_data(Mcap_960), "data.frame") #sample df
  
    #adonis by colony level
    adonis2(Mcap_960.dist ~ Location, data = samp.Mcap_960)
    
        #anova
     aov.propD = aov(Prop.D ~Location, data=samp.Mcap_970)
      summary(aov.propD)
      TukeyHSD(aov.propD)
      
#976
Mcap_976 <- subset_samples(DIV_RelA, TagID =="976") #Subset by colony  
  Mcap_976.dist <- phyloseq::distance(Mcap_976, method = "bray")
  samp.Mcap_976<- as(sample_data(Mcap_976), "data.frame") #sample df
  
    #adonis by colony level
    adonis2(Mcap_976.dist ~ Location, data = samp.Mcap_976)
    
        #anova
     aov.propD = aov(Prop.D ~Location, data=samp.Mcap_970)
      summary(aov.propD)
      TukeyHSD(aov.propD)
      
#985
Mcap_985 <- subset_samples(DIV_RelA, TagID =="985") #Subset by colony  
  Mcap_985.dist <- phyloseq::distance(Mcap_985, method = "bray")
  samp.Mcap_985<- as(sample_data(Mcap_985), "data.frame") #sample df
  
    #adonis by colony level
    adonis2(Mcap_985.dist ~ Location, data = samp.Mcap_985)
    
        #anova
     aov.propD = aov(Prop.D ~Location, data=samp.Mcap_970)
      summary(aov.propD)
      TukeyHSD(aov.propD)
      
#964
Mcap_964 <- subset_samples(DIV_RelA, TagID =="964") #Subset by colony  
  Mcap_964.dist <- phyloseq::distance(Mcap_964, method = "bray")
  samp.Mcap_964<- as(sample_data(Mcap_964), "data.frame") #sample df
  
    #adonis by colony level
    adonis2(Mcap_964.dist ~ Location, data = samp.Mcap_964)
    
        #anova
     aov.propD = aov(Prop.D ~Location, data=samp.Mcap_970)
      summary(aov.propD)
      TukeyHSD(aov.propD)
      
#959
Mcap_959 <- subset_samples(DIV_RelA, TagID =="959") #Subset by colony  
  Mcap_959.dist <- phyloseq::distance(Mcap_959, method = "bray")
  samp.Mcap_959<- as(sample_data(Mcap_959), "data.frame") #sample df
  
    #adonis by colony level
    adonis2(Mcap_959.dist ~ Location, data = samp.Mcap_959)
    
        #anova
     aov.propD = aov(Prop.D ~Location, data=samp.Mcap_970)
      summary(aov.propD)
      TukeyHSD(aov.propD)
      
#980
Mcap_980 <- subset_samples(DIV_RelA, TagID =="980") #Subset by colony  
  Mcap_980.dist <- phyloseq::distance(Mcap_980, method = "bray")
  samp.Mcap_980<- as(sample_data(Mcap_980), "data.frame") #sample df
  
    #adonis by colony level
    adonis2(Mcap_980.dist ~ Location, data = samp.Mcap_980)
  
        #anova
     aov.propD = aov(Prop.D ~Location, data=samp.Mcap_970)
      summary(aov.propD)
      TukeyHSD(aov.propD)
```
Plots DIVS by colony
```{r}  

#for the legend
 plot_bar(Mcap_970,fill = "DIV")+
      geom_bar(aes(color=DIV, fill=DIV), stat="identity", position="stack")

Mcap_970_plot<-plot_bar(Mcap_970, "Sample_name", fill="DIV", title="Mcap_970")+
   theme(legend.position="none");Mcap_970_plot
Mcap_965_plot<-plot_bar(Mcap_965, "Sample_name", fill="DIV", title="Mcap_965")+
   theme(legend.position="none");Mcap_965_plot
Mcap_969_plot<-plot_bar(Mcap_969, "Sample_name", fill="DIV", title="Mcap_969")+
   theme(legend.position="none");Mcap_969_plot
Mcap_972_plot<-plot_bar(Mcap_972, "Sample_name", fill="DIV", title="Mcap_972")+
   theme(legend.position="none");Mcap_972_plot
Mcap_971_plot<-plot_bar(Mcap_971, "Sample_name", fill="DIV", title="Mcap_971")+
   theme(legend.position="none");Mcap_971_plot
Mcap_968_plot<-plot_bar(Mcap_968, "Sample_name", fill="DIV", title="Mcap_968")+
   theme(legend.position="none");Mcap_968_plot
Mcap_966_plot<-plot_bar(Mcap_966, "Sample_name", fill="DIV", title="Mcap_966")+
   theme(legend.position="none");Mcap_966_plot
Mcap_978_plot<-plot_bar(Mcap_978, "Sample_name", fill="DIV", title="Mcap_978")+
   theme(legend.position="none");Mcap_978_plot
Mcap_963_plot<-plot_bar(Mcap_963, "Sample_name", fill="DIV", title="Mcap_963")+
   theme(legend.position="none");Mcap_963_plot
Mcap_961_plot<-plot_bar(Mcap_961, "Sample_name", fill="DIV", title="Mcap_961")+
   theme(legend.position="none");Mcap_961_plot
Mcap_981_plot<-plot_bar(Mcap_981, "Sample_name", fill="DIV", title="Mcap_981")+
   theme(legend.position="none");Mcap_981_plot
Mcap_967_plot<-plot_bar(Mcap_967, "Sample_name", fill="DIV", title="Mcap_967")+
   theme(legend.position="none");Mcap_967_plot
Mcap_983_plot<-plot_bar(Mcap_983, "Sample_name", fill="DIV", title="Mcap_983")+
   theme(legend.position="none");Mcap_983_plot
Mcap_974_plot<-plot_bar(Mcap_974, "Sample_name", fill="DIV", title="Mcap_974")+
   theme(legend.position="none");Mcap_974_plot
Mcap_984_plot<-plot_bar(Mcap_984, "Sample_name", fill="DIV", title="Mcap_984")+
   theme(legend.position="none");Mcap_984_plot
Mcap_962_plot<-plot_bar(Mcap_962, "Sample_name", fill="DIV", title="Mcap_962")+
   theme(legend.position="none");Mcap_962_plot
Mcap_957_plot<-plot_bar(Mcap_957, "Sample_name", fill="DIV", title="Mcap_957")+
   theme(legend.position="none");Mcap_957_plot
Mcap_945_plot<-plot_bar(Mcap_945, "Sample_name", fill="DIV", title="Mcap_945")+
   theme(legend.position="none");Mcap_945_plot
Mcap_960_plot<-plot_bar(Mcap_960, "Sample_name", fill="DIV", title="Mcap_960")+
   theme(legend.position="none");Mcap_960_plot
Mcap_976_plot<-plot_bar(Mcap_976, "Sample_name", fill="DIV", title="Mcap_976")+
   theme(legend.position="none");Mcap_976_plot
Mcap_985_plot<-plot_bar(Mcap_985, "Sample_name", fill="DIV", title="Mcap_985")+
   theme(legend.position="none");Mcap_985_plot
Mcap_964_plot<-plot_bar(Mcap_964, "Sample_name", fill="DIV", title="Mcap_964")+
   theme(legend.position="none");Mcap_964_plot
Mcap_985_plot<-plot_bar(Mcap_985, "Sample_name", fill="DIV", title="Mcap_985")+
   theme(legend.position="none");Mcap_985_plot
Mcap_959_plot<-plot_bar(Mcap_959, "Sample_name", fill="DIV", title="Mcap_959")+
   theme(legend.position="none");Mcap_959_plot
Mcap_980_plot<-plot_bar(Mcap_980, "Sample_name", fill="DIV", title="Mcap_980")+
   theme(legend.position="none");Mcap_980_plot

#name of sample location on C/Ds
Mcap_970_plotB<-plot_bar(Mcap_970, "LocSamp", fill="DIV", title="Mcap_970")+
   theme(legend.position="none");Mcap_970_plotB


Mcap_DIV_plot1 <- ggarrange(Mcap_970_plot, Mcap_965_plot,Mcap_969_plot,Mcap_972_plot, Mcap_971_plot,Mcap_968_plot,Mcap_966_plot,Mcap_978_plot,
                    #labels = c("A", "B", "C","D","E","F"),
                    ncol = 4, nrow = 2);Mcap_DIV_plot1

Mcap_DIV_plot2 <- ggarrange(Mcap_963_plot, Mcap_961_plot,Mcap_981_plot,Mcap_967_plot,
Mcap_983_plot,Mcap_974_plot,Mcap_984_plot,Mcap_962_plot,
                    #labels = c("A", "B", "C","D","E","F"),
                    ncol = 4, nrow = 2);Mcap_DIV_plot2

Mcap_DIV_plot3 <- ggarrange(Mcap_957_plot,Mcap_945_plot,Mcap_960_plot,Mcap_976_plot,
Mcap_985_plot,Mcap_964_plot,Mcap_985_plot,Mcap_964_plot,Mcap_985_plot,Mcap_959_plot,Mcap_980_plot,
                    #labels = c("A", "B", "C","D","E","F"),
                    ncol = 4, nrow = 3);Mcap_DIV_plot3

```


#Plots CLADE

```{r}   

# library("RColorBrewer")
# getPalette = colorRampPalette(brewer.pal(8, "Dark2"))
# 
# speciesList = unique(tax_table(Pro_RelA)[,"clade"])
# speciesPalette = getPalette(length(speciesList))
# names(speciesPalette) = speciesList
# 
# scale_color_manual(values=speciesPalette)
# scale_fill_manual(values= speciesPalette)

#this works but you need better pallet color = grDevices::colors()[grep('gr(a|e)y', grDevices::colors(), invert = T)]
clade.colors <- c(C = "deepskyblue", D = "orange")



# pretty the axis labels with ggplot2
# Mcap_970_clade_plot + theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))+
#   scale_fill_brewer(palette="Paired")


Mcap_970_clade_plot<-plot_bar(Mcap_970_Pro, "LocSamp",fill="clade", title="Mcap_970_clade")+
  scale_fill_manual(values=clade.colors)+
   theme(legend.position="none") + 
  theme(axis.text.x = element_text(angle = 90))+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black"));Mcap_970_clade_plot
ggsave("Mcap_970_clade_plot.pdf")


Mcap_965_clade_plot<-plot_bar(Mcap_965_Pro, "LocSamp", fill="clade", title="Mcap_965_clade")+
    scale_fill_manual(values=clade.colors)+
   theme(legend.position="none") +  theme(axis.text.x = element_text(angle = 90))+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black"));Mcap_965_clade_plot
ggsave("Mcap_965_clade_plot.pdf")


Mcap_969_clade_plot<-plot_bar(Mcap_969_Pro, "LocSamp", fill="clade", title="Mcap_969_clade")+
    scale_fill_manual(values=clade.colors)+
   theme(legend.position="none") +  theme(axis.text.x = element_text(angle = 90))+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black"));Mcap_969_clade_plot
ggsave("Mcap_969_clade_plot.pdf")


Mcap_972_clade_plot<-plot_bar(Mcap_972_Pro, "LocSamp", fill="clade", title="Mcap_972_clade")+
    scale_fill_manual(values=clade.colors)+
   theme(legend.position="none") +  theme(axis.text.x = element_text(angle = 90))+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black"));Mcap_972_clade_plot
ggsave("Mcap_972_clade_plot.pdf")


Mcap_971_clade_plot<-plot_bar(Mcap_971_Pro, "LocSamp", fill="clade", title="Mcap_971_clade")+
    scale_fill_manual(values=clade.colors)+
   theme(legend.position="none") +  theme(axis.text.x = element_text(angle = 90))+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black"));Mcap_971_clade_plot
ggsave("Mcap_971_clade_plot.pdf")


Mcap_968_clade_plot<-plot_bar(Mcap_968_Pro, "LocSamp", fill="clade", title="Mcap_968_clade")+
    scale_fill_manual(values=clade.colors)+
   theme(legend.position="none") +  theme(axis.text.x = element_text(angle = 90))+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black"));Mcap_968_clade_plot
ggsave("Mcap_968_clade_plot.pdf")


Mcap_966_clade_plot<-plot_bar(Mcap_966_Pro, "LocSamp", fill="clade", title="Mcap_966_clade")+
    scale_fill_manual(values=clade.colors)+
   theme(legend.position="none") +  theme(axis.text.x = element_text(angle = 90))+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black"));Mcap_966_clade_plot
ggsave("Mcap_966_clade_plot.pdf")


Mcap_978_clade_plot<-plot_bar(Mcap_978_Pro, "LocSamp", fill="clade", title="Mcap_978_clade")+
    scale_fill_manual(values=clade.colors)+
   theme(legend.position="none") +  theme(axis.text.x = element_text(angle = 90))+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black"));Mcap_978_clade_plot
ggsave("Mcap_978_clade_plot.pdf")


Mcap_963_clade_plot<-plot_bar(Mcap_963_Pro, "LocSamp", fill="clade", title="Mcap_963_clade")+
    scale_fill_manual(values=clade.colors)+
   theme(legend.position="none") +  theme(axis.text.x = element_text(angle = 90))+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black"));Mcap_963_clade_plot
ggsave("Mcap_963_clade_plot.pdf")


Mcap_961_clade_plot<-plot_bar(Mcap_961_Pro, "LocSamp", fill="clade", title="Mcap_961_clade")+
    scale_fill_manual(values=clade.colors)+
   theme(legend.position="none") +  theme(axis.text.x = element_text(angle = 90))+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black"));Mcap_961_clade_plot
ggsave("Mcap_961_clade_plot.pdf")


Mcap_981_clade_plot<-plot_bar(Mcap_981_Pro, "LocSamp", fill="clade", title="Mcap_981_clade")+
    scale_fill_manual(values=clade.colors)+
   theme(legend.position="none") +  theme(axis.text.x = element_text(angle = 90))+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black"));Mcap_981_clade_plot
ggsave("Mcap_981_clade_plot.pdf")


Mcap_967_clade_plot<-plot_bar(Mcap_967_Pro, "LocSamp", fill="clade", title="Mcap_967_clade")+
    scale_fill_manual(values=clade.colors)+
   theme(legend.position="none") +  theme(axis.text.x = element_text(angle = 90))+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black"));Mcap_967_clade_plot
ggsave("Mcap_967_clade_plot.pdf")


Mcap_983_clade_plot<-plot_bar(Mcap_983_Pro, "LocSamp", fill="clade", title="Mcap_983_clade")+
    scale_fill_manual(values=clade.colors)+
   theme(legend.position="none") +  theme(axis.text.x = element_text(angle = 90))+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black"));Mcap_983_clade_plot
ggsave("Mcap_983_clade_plot.pdf")


Mcap_974_clade_plot<-plot_bar(Mcap_974_Pro, "LocSamp", fill="clade", title="Mcap_974_clade")+
    scale_fill_manual(values=clade.colors)+
   theme(legend.position="none") +  theme(axis.text.x = element_text(angle = 90))+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black"));Mcap_974_clade_plot
ggsave("Mcap_974_clade_plot.pdf")


Mcap_984_clade_plot<-plot_bar(Mcap_984_Pro, "LocSamp", fill="clade", title="Mcap_984_clade")+
    scale_fill_manual(values=clade.colors)+
   theme(legend.position="none") +  theme(axis.text.x = element_text(angle = 90))+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black"));Mcap_984_clade_plot
ggsave("Mcap_984_clade_plot.pdf")


Mcap_962_clade_plot<-plot_bar(Mcap_962_Pro, "LocSamp", fill="clade", title="Mcap_962_clade")+
    scale_fill_manual(values=clade.colors)+
   theme(legend.position="none") +  theme(axis.text.x = element_text(angle = 90))+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black"));Mcap_962_clade_plot
ggsave("Mcap_962_clade_plot.pdf")


Mcap_957_clade_plot<-plot_bar(Mcap_957_Pro, "LocSamp", fill="clade", title="Mcap_957_clade")+
    scale_fill_manual(values=clade.colors)+
   theme(legend.position="none") +  theme(axis.text.x = element_text(angle = 90))+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black"));Mcap_957_clade_plot
ggsave("Mcap_957_clade_plot.pdf")


Mcap_945_clade_plot<-plot_bar(Mcap_945_Pro, "LocSamp", fill="clade", title="Mcap_945_clade")+
    scale_fill_manual(values=clade.colors)+
   theme(legend.position="none") +  theme(axis.text.x = element_text(angle = 90))+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black"));Mcap_945_clade_plot
ggsave("Mcap_945_clade_plot.pdf")


Mcap_960_clade_plot<-plot_bar(Mcap_960_Pro, "LocSamp", fill="clade", title="Mcap_960_clade")+
    scale_fill_manual(values=clade.colors)+
   theme(legend.position="none") +  theme(axis.text.x = element_text(angle = 90))+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black"));Mcap_960_clade_plot
ggsave("Mcap_960_clade_plot.pdf")


Mcap_976_clade_plot<-plot_bar(Mcap_976_Pro, "LocSamp", fill="clade", title="Mcap_976_clade")+
    scale_fill_manual(values=clade.colors)+
   theme(legend.position="none") +  theme(axis.text.x = element_text(angle = 90))+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black"));Mcap_976_clade_plot
ggsave("Mcap_976_clade_plot.pdf")


Mcap_985_clade_plot<-plot_bar(Mcap_985_Pro, "LocSamp", fill="clade", title="Mcap_985_clade")+
    scale_fill_manual(values=clade.colors)+
   theme(legend.position="none") +  theme(axis.text.x = element_text(angle = 90))+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black"));Mcap_985_clade_plot
ggsave("Mcap_985_clade_plot.pdf")


Mcap_964_clade_plot<-plot_bar(Mcap_964_Pro, "LocSamp", fill="clade", title="Mcap_964_clade")+
    scale_fill_manual(values=clade.colors)+
   theme(legend.position="none") +  theme(axis.text.x = element_text(angle = 90))+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black"));Mcap_964_clade_plot
ggsave("Mcap_964_clade_plot.pdf")


Mcap_985_clade_plot<-plot_bar(Mcap_985_Pro, "LocSamp", fill="clade", title="Mcap_985_clade")+
    scale_fill_manual(values=clade.colors)+
   theme(legend.position="none") +  theme(axis.text.x = element_text(angle = 90))+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black"));Mcap_985_clade_plot
ggsave("Mcap_985_clade_plot.pdf")


Mcap_959_clade_plot<-plot_bar(Mcap_959_Pro, "LocSamp", fill="clade", title="Mcap_959_clade")+
    scale_fill_manual(values=clade.colors)+
   theme(legend.position="none") +  theme(axis.text.x = element_text(angle = 90))+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black"));Mcap_959_clade_plot
ggsave("Mcap_959_clade_plot.pdf")


Mcap_980_clade_plot<-plot_bar(Mcap_980_Pro, "LocSamp", fill="clade", title="Mcap_980_clade")+
    scale_fill_manual(values=clade.colors)+
   theme(legend.position="none")+theme(axis.text.x = element_text(angle = 90))+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black"));Mcap_980_clade_plot
ggsave("Mcap_980_clade_plot.pdf")

```



Plot all clade level by colony
```{r} 
theme_set(theme_classic())
library(ggpubr)

library(ggarrange)


figureMCL1 <- ggarrange(Mcap_970_clade_plot, Mcap_965_clade_plot, Mcap_969_clade_plot,Mcap_972_clade_plot, 
                               Mcap_970_PRO_plot, Mcap_965_PRO_plot, Mcap_969_PRO_plot, Mcap_972_PRO_plot, 
                               Mcap_970_plot, Mcap_965_plot, Mcap_969_plot, Mcap_972_plot, 
                    ncol = 4, nrow = 3);figureMCL1

figureMCL2 <- ggarrange(Mcap_971_clade_plot,Mcap_968_clade_plot,Mcap_966_clade_plot,Mcap_978_clade_plot, 
                        Mcap_971_PRO_plot,Mcap_968_PRO_plot,Mcap_966_PRO_plot,Mcap_978_PRO_plot, 
                        Mcap_971_plot,Mcap_968_plot,Mcap_966_plot,Mcap_978_plot, 
                    ncol = 4, nrow = 3);figureMCL2

figureMCL3 <- ggarrange(Mcap_963_clade_plot, Mcap_961_clade_plot,Mcap_981_clade_plot,Mcap_967_clade_plot,
                        Mcap_963_PRO_plot, Mcap_961_PRO_plot,Mcap_981_PRO_plot,Mcap_967_PRO_plot,
                        Mcap_963_plot, Mcap_961_plot,Mcap_981_plot,Mcap_967_plot,
                    ncol = 4, nrow = 3);figureMCL3

figureMCL4 <- ggarrange(Mcap_983_clade_plot, Mcap_974_clade_plot,Mcap_984_clade_plot,Mcap_962_clade_plot, 
                        Mcap_983_PRO_plot, Mcap_974_PRO_plot,Mcap_984_PRO_plot,Mcap_962_PRO_plot, 
                        Mcap_983_plot,Mcap_974_plot,Mcap_984_plot,Mcap_962_plot, 
                    ncol = 4, nrow = 3);figureMCL4

figureMCL5 <- ggarrange(Mcap_957_clade_plot, Mcap_945_clade_plot,Mcap_960_clade_plot,Mcap_976_clade_plot,
                        Mcap_957_PRO_plot,Mcap_945_PRO_plot,Mcap_960_PRO_plot,Mcap_976_PRO_plot,
                        Mcap_957_plot,Mcap_945_plot,Mcap_960_plot,Mcap_976_plot,
                    ncol = 4, nrow = 3);figureMCL5


figureMCL6 <- ggarrange(Mcap_985_clade_plot, Mcap_964_clade_plot, Mcap_959_clade_plot,Mcap_980_clade_plot,
                        Mcap_985_PRO_plot, Mcap_964_PRO_plot, Mcap_959_PRO_plot,Mcap_980_PRO_plot,
                        Mcap_985_plot,Mcap_964_plot,Mcap_959_plot,Mcap_980_plot,
                    ncol = 4, nrow = 3);figureMCL6



```

#probability of 1 sample correctly identifying dom symbiont
```{r}
probCD<-read.csv("propCD for probability.csv")

as_tibble(probCD)

#make a dom col for each sample 
probCD<-data.ra[c(16,25,31,32)]

probCD$dom.samp<- with(data.ra, ifelse(
  Prop.C>=0.5,"C", ifelse(
    Prop.C<=0.5, "D","NA"))
  )

#get meta per colony to calc dom zoox per colony level
col.dom<-data.ra[c(16,31,32)]

col.dom2<-  col.dom %>% #mean by CD by genotype
  group_by(ColonyDNA.ID) %>%
   summarise_at(vars("Prop.C", "Prop.D"), mean)
  
col.dom2$dom.colony<- with(col.dom2, ifelse( #col dom 
  Prop.C>=0.5,"C", ifelse(
    Prop.C<=0.5, "D","NA"))
  )
col.dom3<-col.dom2[c(1,4)] #keep what you need

probCD2<-merge(probCD, col.dom3, by="ColonyDNA.ID", all.x=T) #merge

probCD2<- transform(
  probCD2, Match= ifelse(dom.samp==dom.colony, "Y", "N"))

table(probCD2['Match']) # how many match or not. 
#354 Yes, 21 no
# 5 of the 24 colonies had at least 1 sample taht did not predict. it ranged from 1 to 

probCD3<-probCD2 #make copy, fig probabilitiy by colony

probCD3<-  probCD3 %>% #mean by  by genotype
  group_by(ColonyDNA.ID) %>%
   summarise_at(vars("Prop.C", "Prop.D"), mean)
write.csv(probCD3,"probCD3.csv")

```





Ordination OLD
```{r}
plot_ordination(coralDIV2.prune, ordinate(coralDIV2.prune, "MDS"), color = "TagID") + geom_point(size = 5)
plot_heatmap(coralDIV2.prune, "NMDS", "bray", "TagID", "DIV")

GP.ord <- ordinate(coralDIV2.prune, "NMDS", "bray")
p1 = plot_ordination(coralDIV2.prune, GP.ord, type="samples", color="TagID", title="taxa")
print(p1)

p2 = plot_ordination(coralDIV2.prune, GP.ord, type="samples", color="TagID", shape="TagID") 
p2 + geom_polygon(aes(fill=SampleType)) + geom_point(size=5) + ggtitle("samples")
```



# PERMANOVA coralDIV2.prune (older)

Write specific questions to answer:
-do algal communities differ between colonies? 
-do algal communities differ within colonies
-do they differ between C-only and D-only? 
-is there a dominant C type or D type
- check hypotheses based on location (tips vs branches) across entire dataset and by dom clade
```{r}            
# use this  
otu_table(DIV_RelA)[1:5, 1:5] #check rela worked

#bray curtis presence-absense and abundance
 
  DIV_RelA = prune_taxa(taxa_sums(DIV_RelA) > 0, DIV_RelA) #this removes any OTU with 0s

#bray curtis presence-absense and abundance

#all speices
set.seed(300)

#make bray curtis data matrix
bc.all <- phyloseq::distance(DIV_RelA, method = "bray")
  samp.df <- as(sample_data(coralDIV2.prune_stats), "data.frame") #sample df
  
  samp.df$TagID<-as.factor(samp.df$TagID)
    samp.df$Land_Ocean<-as.factor(samp.df$Land_Ocean)
    samp.df$SampLoc<-as.factor(samp.df$SampLoc)
    samp.df$Location<-paste(samp.df$SampLoc, samp.df$Sub.loc) #sample location and sub location
  
#adonis test
adonis2(bc.all ~ TagID*Location, data = samp.df) #all sig
    # genotype, sample location and interaction all significant. 

# Homogeneity of dispersion test
beta.colony <- betadisper(bc.all, samp.df$TagID)
perm<-permutest(beta.colony, pairwise = T) 
(bc.all.HSD <- TukeyHSD(beta.colony)) #do you need?
plot(bc.all.HSD)


#Ordination NMDS for all species
set.seed(30)
ord.DIV_bc.all <- ordinate(coralDIV2.prune_stats, "NMDS", "bray", trymax = 300)  ### NO CONVERGENCE
stressplot(ord.DIV_bc.all)
ord.DIV_bc.all <- as.data.frame(cbind(vegan::scores(ord.DIV_bc.all, display="sites"))) #make df
ord.DIV_bc.all$TagID <- samp.df$TagID
ord.DIV_bc.all$SampLoc <- samp.df$SampLoc
ord.DIV_bc.all$Zoox <- samp.df$Zoox

ggplot(ord.DIV_bc.all, aes(x = NMDS1, y = NMDS2)) + 
  geom_point(aes(colour = TagID), size = 4,show.legend=T) +
  #scale_color_manual(values=Sp.colors)+
  # geom_text(label = rownames(Clade), nudge_x = 0.05, nudge_y = 0.05,check_overlap = T) +
  stat_ellipse(aes(x = NMDS1, y = NMDS2, colour = TagID), linetype = 2,show.legend=T) +
  ggtitle("NMDS its2 Bray Curtis genotype ") +
  theme_classic()
#ggsave("bc_all.pdf")

ggplot(ord.DIV_bc.all, aes(x = NMDS1, y = NMDS2, color = TagID )) +
  geom_point(aes(colour=TagID), size=4) +
  stat_ellipse(geom = "polygon",
               aes(fill = TagID), 
               alpha = 0.25)+
    theme_classic()

zoox.cols <- c("C" = "green2","CD"="darkslateblue","D"="darkorange")

ggplot(ord.DIV_bc.all, aes(x = NMDS1, y = NMDS2, color = Zoox )) +
  geom_point(aes(colour=Zoox), size=5, alpha=0.8) +
      scale_color_manual(values=zoox.cols)+
  # stat_ellipse(geom = "polygon",
  #              aes(fill = Zoox), 
  #              alpha = 0.2)+
    theme_classic()

######### Try by Cs only #### 
coralDIV2.prune_stats_C<-subset_samples(coralDIV2.prune_stats, Zoox=="C")
coralDIV2.prune_stats_C = prune_taxa(taxa_sums(coralDIV2.prune_stats_C) > 0, coralDIV2.prune_stats_C)
  
set.seed(30)
ord.DIV_bc.C <- ordinate(coralDIV2.prune_stats_C, "NMDS", "bray", trymax = 300)  ### NO CONVERGENCE
stressplot(ord.DIV_bc.C)
  samp.df.C <- as(sample_data(coralDIV2.prune_stats_C), "data.frame") #sample df

ord.DIV_bc.C <- as.data.frame(cbind(vegan::scores(ord.DIV_bc.C, display="sites"))) #make df
ord.DIV_bc.C$TagID <- samp.df.C$TagID
ord.DIV_bc.C$TagID<-as.factor(ord.DIV_bc.C$TagID)
ord.DIV_bc.C$SampLoc <- samp.df.C$SampLoc
ord.DIV_bc.C$Location<-samp.df.C$Sub.loc
ord.DIV_bc.C$Code<-paste(ord.DIV_bc.C$SampLoc, ord.DIV_bc.C$Location)
ord.DIV_bc.C$Code<-as.factor(ord.DIV_bc.C$Code)

ggplot(ord.DIV_bc.C, aes(x = NMDS1, y = NMDS2)) + 
  geom_point(aes(colour = TagID), size = 4,show.legend=T) +
  #scale_color_manual(values=Sp.colors)+
  # geom_text(label = rownames(Clade), nudge_x = 0.05, nudge_y = 0.05,check_overlap = T) +
  stat_ellipse(aes(x = NMDS1, y = NMDS2, colour = TagID),show.legend=T) +
  ggtitle("NMDS its2 C only ") +
  theme_classic()
#ggsave("bc_all.pdf")

ggplot(ord.DIV_bc.C, aes(x = NMDS1, y = NMDS2, color = Code, linetype=Code)) +
  geom_point(aes(shape=Code), size=4) +
  stat_ellipse(geom = "polygon",
               aes(fill = Code), 
               alpha = 0.25)+
    theme_classic()

ggplot(ord.DIV_bc.C, aes(x = NMDS1, y = NMDS2)) + 
  geom_point(aes(colour = Code), size = 4,show.legend=T) +
  #scale_Dolor_manual(values=Sp.Dolors)+
  # geom_text(label = rownames(Clade), nudge_x = 0.05, nudge_y = 0.05,check_overlap = T) +
  # stat_ellipse(aes(x = NMDS1, y = NMDS2, colour = Code),show.legend=T) +
    geom_mark_hull(concavity = 5,expand=0,radius=0,aes(fill=Code))+
  ggtitle("NMDS its2 C only ") +
  theme_classic()
#ggsave("bc_all.pdf")



ggplot(ord.DIV_bc.C, aes(x = NMDS1, y = NMDS2)) + 
  geom_point(aes(colour = Code), size = 4,show.legend=T) +
  #scale_Dolor_manual(values=Sp.Dolors)+
  # geom_text(label = rownames(Clade), nudge_x = 0.05, nudge_y = 0.05,check_overlap = T) +
  # stat_ellipse(aes(x = NMDS1, y = NMDS2, colour = Code),show.legend=T) +
  geom_mark_ellipse(expand = 0,aes(fill=Code))+
  ggtitle("NMDS its2 C only ") +
  theme_classic()
#ggsave("bc_all.pdf")




######### Try by Ds only #### 
coralDIV2.prune_stats_D<-subset_samples(coralDIV2.prune_stats, Zoox=="D")
coralDIV2.prune_stats_D = prune_taxa(taxa_sums(coralDIV2.prune_stats_D) > 0, coralDIV2.prune_stats_D)
  
set.seed(300)
ord.DIV_bc.D <- ordinate(coralDIV2.prune_stats_D, "NMDS", "bray", trymax = 500)  #
stressplot(ord.DIV_bc.D)
  samp.df.D <- as(sample_data(coralDIV2.prune_stats_D), "data.frame") #sample df

ord.DIV_bc.D <- as.data.frame(cbind(vegan::scores(ord.DIV_bc.D, display="sites"))) #make df
ord.DIV_bc.D$TagID <- samp.df.D$TagID
ord.DIV_bc.D$TagID<-as.factor(ord.DIV_bc.D$TagID)
ord.DIV_bc.D$SampLoc <- samp.df.D$SampLoc
ord.DIV_bc.D$Location<-samp.df.D$Sub.loc
ord.DIV_bc.D$Code<-paste(ord.DIV_bc.D$SampLoc, ord.DIV_bc.D$Location)
ord.DIV_bc.D$Code<-as.factor(ord.DIV_bc.D$Code)

ggplot(ord.DIV_bc.D, aes(x = NMDS1, y = NMDS2)) + 
  geom_point(aes(colour = TagID), size = 4,show.legend=T) +
  #scale_Dolor_manual(values=Sp.Dolors)+
  # geom_text(label = rownames(Clade), nudge_x = 0.05, nudge_y = 0.05,check_overlap = T) +
  stat_ellipse(aes(x = NMDS1, y = NMDS2, colour = TagID),show.legend=T) +
  ggtitle("NMDS its2 D only ") +
  theme_classic()
#ggsave("bc_all.pdf")


library(ggalt)
library(ggforce)
library(concaveman)

ggplot(ord.DIV_bc.D, aes(x = NMDS1, y = NMDS2)) + 
  geom_point(aes(colour = Code), size = 4,show.legend=T) +
  #scale_Dolor_manual(values=Sp.Dolors)+
  # geom_text(label = rownames(Clade), nudge_x = 0.05, nudge_y = 0.05,check_overlap = T) +
  # stat_ellipse(aes(x = NMDS1, y = NMDS2, colour = Code),show.legend=T) +
    geom_mark_hull(concavity = 5,expand=0,radius=0,aes(fill=Code))+
  ggtitle("NMDS its2 D only ") +
  theme_classic()
#ggsave("bc_all.pdf")


ggplot(ord.DIV_bc.D, aes(x = NMDS1, y = NMDS2, color = Code, linetype=Code)) +
  geom_point(aes(colour=Code), size=4) +
  stat_ellipse(geom = "polygon",
               aes(fill = Code), 
               alpha = 0.25)+
    theme_classic()





#bray curtis presence-absense and abundance

#all speices
set.seed(30)

#make bray curtis data matrix
bc.all <- phyloseq::distance(DIV_RelA_stats, method = "bray")
  samp.df <- as(sample_data(DIV_RelA_stats), "data.frame") #sample df
#adonis test
adonis(bc.all ~ Species*Time.Point*Treatment, data = samp.df)
    

# Homogeneity of dispersion test
betaAll <- betadisper(bc.all, samp.df$Species)
permutest(betaAll, pairwise = T) 
(bc.all.HSD <- TukeyHSD(betaAll)) #do you need?
plot(bc.all.HSD)


#Ordination NMDS for all species
set.seed(30)
ord.DIV_RelA_stats <- ordinate(DIV_RelA_stats, "NMDS", "bray", trymax = 100) 
stressplot(ord.DIV_RelA_stats)
scores.ord.DIV_RelA_stats <- as.data.frame(cbind(vegan::scores(ord.DIV_RelA_stats, display="sites"))) #make df
scores.ord.DIV_RelA_stats$Treatment <- samp.df$Treatment
scores.ord.DIV_RelA_stats$Species <- samp.df$Species
scores.ord.DIV_RelA_stats$Clade <- samp.df$Clade
scores.ord.DIV_RelA_stats$Time.Point <- samp.df$Time.Point

ggplot(scores.ord.DIV_RelA_stats, aes(x = NMDS1, y = NMDS2)) + 
  geom_point(aes(colour = Species), size = 4) +
  #scale_color_manual(values=Mcap.Parent.colors)+
  #geom_text(label = rownames(scores), nudge_x = 0.05, nudge_y = 0.05,check_overlap = T) +
  #stat_ellipse(aes(x = NMDS1, y = NMDS2, colour = Treatment), linetype = 2) +
  ggtitle("NMDS its2 Bray Curtis") +
  theme_classic()
#ggsave("bc_all.pdf")

ggplot(scores.ord.DIV_RelA_stats, aes(x = NMDS1, y = NMDS2)) + 
  geom_point(aes(colour = Clade, shape=Species), size = 4) +
  #scale_color_manual(values=Mcap.Parent.colors)+
  #geom_text(label = rownames(scores), nudge_x = 0.05, nudge_y = 0.05,check_overlap = T) +
  #stat_ellipse(aes(x = NMDS1, y = NMDS2, colour = Treatment), linetype = 2) +
  ggtitle("NMDS its2 Bray Curtis") +
  theme_classic()
#ggsave("bc_all.pdf")



######### Try by CDs only #### 
coralDIV2.prune_stats_CD<-subset_samples(coralDIV2.prune_stats, Zoox=="CD")
coralDIV2.prune_stats_CD = prune_taxa(taxa_sums(coralDIV2.prune_stats_CD) > 0, coralDIV2.prune_stats_CD)
  
set.seed(30)
ord.DIV_bc.CD <- ordinate(coralDIV2.prune_stats_CD, "NMDS", "bray", trymax = 300)  ###  CONVERGENCE
stressplot(ord.DIV_bc.CD)
  samp.df.CD <- as(sample_data(coralDIV2.prune_stats_CD), "data.frame") #sample df

ord.DIV_bc.CD <- as.data.frame(cbind(vegan::scores(ord.DIV_bc.CD, display="sites"))) #make df
ord.DIV_bc.CD$TagID <- samp.df.CD$TagID
ord.DIV_bc.CD$TagID<-as.factor(ord.DIV_bc.CD$TagID)
ord.DIV_bc.CD$SampLoc <- samp.df.CD$SampLoc
ord.DIV_bc.CD$Location<-samp.df.CD$Sub.loc
ord.DIV_bc.CD$Code<-paste(ord.DIV_bc.CD$SampLoc, ord.DIV_bc.CD$Location)
ord.DIV_bc.CD$Code<-as.factor(ord.DIV_bc.CD$Code)

ggplot(ord.DIV_bc.CD, aes(x = NMDS1, y = NMDS2)) + 
  geom_point(aes(colour = TagID), size = 4,show.legend=T) +
  #scale_CDolor_manual(values=Sp.CDolors)+
  # geom_text(label = rownames(Clade), nudge_x = 0.05, nudge_y = 0.05,check_overlap = T) +
  stat_ellipse(aes(x = NMDS1, y = NMDS2, colour = TagID),show.legend=T) +
  ggtitle("NMDS its2 CD only ") +
  theme_classic()
#ggsave("bc_all.pdf")

ggplot(ord.DIV_bc.CD, aes(x = NMDS1, y = NMDS2, color = TagID)) +
  geom_point(aes(colour=TagID), size=4, alpha=.2) +
  stat_ellipse(geom = "polygon",
               aes(fill = TagID), 
               alpha = 0.55)+
    theme_classic()

ggplot(ord.DIV_bc.CD, aes(x = NMDS1, y = NMDS2)) + 
  geom_point(aes(colour = Code), size = 4,show.legend=T) +
  #scale_Dolor_manual(values=Sp.Dolors)+
  # geom_text(label = rownames(Clade), nudge_x = 0.05, nudge_y = 0.05,check_overlap = T) +
  # stat_ellipse(aes(x = NMDS1, y = NMDS2, colour = Code),show.legend=T) +
    geom_mark_hull(concavity = 5,expand=0,radius=0,aes(fill=Code))+
  ggtitle("NMDS its2 CD only ") +
  theme_classic()
#ggsave("bc_all.pdf")



##############   BY COLONY   ##################

#945 ####
DIV_RelA_stats_945<-subset_samples(coralDIV2.prune_stats, TagID=="945")
  DIV_RelA_stats_945 = prune_taxa(taxa_sums(DIV_RelA_stats_945) > 0, DIV_RelA_stats_945) #this removes any OTU with 0s
  samp.df_945 <- as(sample_data(DIV_RelA_stats_945), "data.frame") #sample df

#all speices
set.seed(30)

#make bray curtis data matrix
bc.945 <- phyloseq::distance(coralDIV2.prune_stats, method = "bray")
  samp.df_945 <- as(sample_data(coralDIV2.prune_stats), "data.frame") #sample df
#adonis test
adonis(bc.945 ~ SampLoc, data = samp.df_945)
    


#Ordination NMDS for all species
set.seed(30)
ord.DIV_RelA_stats.945 <- ordinate(DIV_RelA_stats_945, "NMDS", "bray", trymax = 100)
  samp.df_945 <- as(sample_data(DIV_RelA_stats_945), "data.frame") #sample df
stressplot(ord.DIV_RelA_stats.945)
ord.DIV_RelA_stats.945 <- as.data.frame(cbind(vegan::scores(ord.DIV_RelA_stats.945, display="sites"))) #make df
ord.DIV_RelA_stats.945$SampLoc <- samp.df_945$SampLoc
ord.DIV_RelA_stats.945$sample_name <- samp.df_945$sample_name
ord.DIV_RelA_stats.945$Code<-paste(ord.DIV_RelA_stats.945$SampLoc,samp.df_945$Sub.loc)

ggplot(ord.DIV_RelA_stats.945, aes(x = NMDS1, y = NMDS2)) + 
  geom_point(aes(colour = Code), size = 7) +
  #scale_color_manual(values=Mcap.Parent.colors)+
  #geom_text(label = rownames(scores), nudge_x = 0.05, nudge_y = 0.05,check_overlap = T) +
  ggtitle("NMDS its2 Bray Curtis 945") +
  theme_classic() 
#ggsave("bc_all.pdf")

ggplot(ord.DIV_RelA_stats.945, aes(x = NMDS1, y = NMDS2)) + 
  geom_point(aes(colour = Code), size = 4,show.legend=T) +
  #scale_Dolor_manual(values=Sp.Dolors)+
  # geom_text(label = rownames(Clade), nudge_x = 0.05, nudge_y = 0.05,check_overlap = T) +
  # stat_ellipse(aes(x = NMDS1, y = NMDS2, colour = Code),show.legend=T) +
  geom_mark_ellipse(expand = 0,aes(fill=Code))+
  ggtitle("NMDS its2 945 only ") +
  theme_classic()
#ggsave("bc_all.pdf")





# for defense old code for code #### 

ggplot(scores.ord.DIV_RelA_stats, aes(x = NMDS1, y = NMDS2, color = Species, linetype=Treatment)) +
  geom_point(aes(shape=Treatment), size=4) +
  stat_ellipse(geom = "polygon",
               aes(fill = Code3), 
               alpha = 0.25)+
    theme_classic()

scores.ord.DIV_RelA_stats$Code4<-paste(scores.ord.DIV_RelA_stats$Species, scores.ord.DIV_RelA_stats$Clade, scores.ord.DIV_RelA_stats$Treatment)

 p<-ggplot(scores.ord.DIV_RelA_stats, aes(x = NMDS1, y = NMDS2, color = Species, linetype=Treatment)) +
  geom_point(aes(shape=Treatment), size=4) +
  stat_ellipse(geom = "polygon",
               aes(fill = Code4), 
               alpha = 0.25)+
    theme_classic()
p+facet_wrap(~Species)



#960 ####
DIV_RelA_stats_960<-subset_samples(coralDIV2.prune_stats, TagID=="960")
  DIV_RelA_stats_960 = prune_taxa(taxa_sums(DIV_RelA_stats_960) > 0, DIV_RelA_stats_960) #this removes any OTU with 0s
  samp.df_960 <- as(sample_data(DIV_RelA_stats_960), "data.frame") #sample df

#all speices
set.seed(30)

#make bray curtis data matrix
bc.960 <- phyloseq::distance(coralDIV2.prune_stats, method = "bray")
  samp.df_960 <- as(sample_data(coralDIV2.prune_stats), "data.frame") #sample df
#adonis test
adonis(bc.960 ~ SampLoc, data = samp.df_960)
    
# Homogeneity of dispersion test
# betaAll <- betadisper(bc.960, samp.df$Species)
# permutest(betaAll, pairwise = T) 
# (bc.all.HSD <- TukeyHSD(betaAll)) #do you need?
# plot(bc.all.HSD)

#Ordination NMDS for all species
set.seed(30)
ord.DIV_RelA_stats.960 <- ordinate(DIV_RelA_stats_960, "NMDS", "bray", trymax = 100) 
stressplot(ord.DIV_RelA_stats.960)
  samp.df_960 <- as(sample_data(DIV_RelA_stats_960), "data.frame") #sample df
ord.DIV_RelA_stats.960 <- as.data.frame(cbind(vegan::scores(ord.DIV_RelA_stats.960, display="sites"))) #make df
ord.DIV_RelA_stats.960$SampLoc <- samp.df_960$SampLoc
ord.DIV_RelA_stats.960$sample_name <- samp.df_960$sample_name
ord.DIV_RelA_stats.960$Location <- samp.df_960$Location

ord.DIV_RelA_stats.960$Code<-paste(ord.DIV_RelA_stats.960$SampLoc, ord.DIV_RelA_stats.960$Location)
ggplot(ord.DIV_RelA_stats.960, aes(x = NMDS1, y = NMDS2)) + 
  geom_point(aes(colour = Location), size = 7) +
  #scale_color_manual(values=Mcap.Parent.colors)+
  #geom_text(label = rownames(scores), nudge_x = 0.05, nudge_y = 0.05,check_overlap = T) +
  ggtitle("NMDS its2 Bray Curtis 960") +
  theme_classic() 

#ggsave("bc_all.pdf")
ggplot(ord.DIV_RelA_stats.960, aes(x = NMDS1, y = NMDS2)) + 
  geom_point(aes(colour = Land_Ocean, shape=Code), size = 4) +
  #scale_color_manual(values=Mcap.Parent.colors)+
  #geom_text(label = rownames(scores), nudge_x = 0.05, nudge_y = 0.05,check_overlap = T) +
  ggtitle("NMDS its2 Bray Curtis 960") +
  theme_classic() 
#ggsave("bc_all.pdf")

ggplot(ord.DIV_RelA_stats.960, aes(x = NMDS1, y = NMDS2)) + 
  geom_point(aes(colour = Code), size = 4,show.legend=T) +
  #scale_Dolor_manual(values=Sp.Dolors)+
  # geom_text(label = rownames(Clade), nudge_x = 0.05, nudge_y = 0.05,check_overlap = T) +
  # stat_ellipse(aes(x = NMDS1, y = NMDS2, colour = Code),show.legend=T) +
  geom_mark_ellipse(expand = 0,aes(fill=Code))+
  ggtitle("NMDS its2 960 only ") +
  theme_classic()
#ggsave("bc_all.pdf")

#970 ####
DIV_RelA_stats_970<-subset_samples(coralDIV2.prune_stats, TagID=="970")
  DIV_RelA_stats_970 = prune_taxa(taxa_sums(DIV_RelA_stats_970) > 0, DIV_RelA_stats_970) #this removes any OTU with 0s
  samp.df_970 <- as(sample_data(DIV_RelA_stats_970), "data.frame") #sample df

#all speices
set.seed(30)

#make bray curtis data matrix
bc.970 <- phyloseq::distance(coralDIV2.prune_stats, method = "bray")
  samp.df_970 <- as(sample_data(coralDIV2.prune_stats), "data.frame") #sample df
#adonis test
adonis(bc.970 ~ SampLoc, data = samp.df_970)
    
# Homogeneity of dispersion test
# betaAll <- betadisper(bc.all, samp.df$Species)
# permutest(betaAll, pairwise = T) 
# (bc.all.HSD <- TukeyHSD(betaAll)) #do you need?
# plot(bc.all.HSD)

#Ordination NMDS for all species
set.seed(30)
ord.DIV_RelA_stats.970 <- ordinate(DIV_RelA_stats_970, "NMDS", "bray", trymax = 100) 
stressplot(ord.DIV_RelA_stats.970)
  samp.df_970 <- as(sample_data(DIV_RelA_stats_970), "data.frame") #sample df

ord.DIV_RelA_stats.970 <- as.data.frame(cbind(vegan::scores(ord.DIV_RelA_stats.970, display="sites"))) #make df
ord.DIV_RelA_stats.970$SampLoc <- samp.df_970$SampLoc
ord.DIV_RelA_stats.970$sample_name <- samp.df_970$sample_name
ord.DIV_RelA_stats.970$Sub.loc <- samp.df_970$Sub.loc
ord.DIV_RelA_stats.970$Location<-samp.df_970$Location

ggplot(ord.DIV_RelA_stats.970, aes(x = NMDS1, y = NMDS2)) + 
  geom_point(aes(colour = Location), size = 7) +
  #scale_color_manual(values=Mcap.Parent.colors)+
  #geom_text(label = rownames(scores), nudge_x = 0.05, nudge_y = 0.05,check_overlap = T) +
  # geom_line(aes(group = Location))+
    geom_mark_ellipse(expand = 0,aes(fill=Location))+
  ggtitle("NMDS its2 Bray Curtis 970") +
  theme_classic() 
#ggsave("bc_all.pdf")

ggplot(ord.DIV_RelA_stats.970, aes(x = NMDS1, y = NMDS2)) + 
  geom_point(aes(colour = Location), size = 4,show.legend=T) +
  #scale_Dolor_manual(values=Sp.Dolors)+
  # geom_text(label = rownames(Clade), nudge_x = 0.05, nudge_y = 0.05,check_overlap = T) +
  stat_ellipse(aes(x = NMDS1, y = NMDS2, colour = Location),show.legend=T) +
  # geom_line(aes(group = Location),color="grey")+
  ggtitle("NMDS its2 970 only ") +
  theme_classic()
#ggsave("bc_all.pdf")



#966 ####
DIV_RelA_stats_966<-subset_samples(coralDIV2.prune_stats, TagID=="966")
  DIV_RelA_stats_966 = prune_taxa(taxa_sums(DIV_RelA_stats_966) > 0, DIV_RelA_stats_966) #this removes any OTU with 0s

#all speices
set.seed(30)

#make bray curtis data matrix
bc.966 <- phyloseq::distance(coralDIV2.prune_stats, method = "bray")
  samp.df_966 <- as(sample_data(coralDIV2.prune_stats), "data.frame") #sample df
#adonis test
adonis(bc.966 ~ SampLoc, data = samp.df_966)
    
#Ordination NMDS for all species
set.seed(30)
ord.DIV_RelA_stats.966 <- ordinate(DIV_RelA_stats_966, "NMDS", "bray", trymax = 100) 
stressplot(ord.DIV_RelA_stats.966)
  samp.df_966 <- as(sample_data(DIV_RelA_stats_966), "data.frame") #sample df
ord.DIV_RelA_stats.966 <- as.data.frame(cbind(vegan::scores(ord.DIV_RelA_stats.966, display="sites"))) #make df
ord.DIV_RelA_stats.966$SampLoc <- samp.df_966$SampLoc
ord.DIV_RelA_stats.966$sample_name <- samp.df_966$sample_name
ord.DIV_RelA_stats.966$Code <- paste(samp.df_966$SampLoc, samp.df_966$Sub.loc)


ggplot(ord.DIV_RelA_stats.966, aes(x = NMDS1, y = NMDS2)) + 
  geom_point(aes(colour = Code), size = 4) +
  #scale_color_manual(values=Mcap.Parent.colors)+
  #geom_text(label = rownames(scores), nudge_x = 0.05, nudge_y = 0.05,check_overlap = T) +
  ggtitle("NMDS its2 Bray Curtis 966") +
  theme_classic() 
#ggsave("bc_all.pdf")


ggplot(ord.DIV_RelA_stats.966, aes(x = NMDS1, y = NMDS2)) + 
  geom_point(aes(colour = Code), size = 4,show.legend=T) +
  #scale_Dolor_manual(values=Sp.Dolors)+
  # geom_text(label = rownames(Clade), nudge_x = 0.05, nudge_y = 0.05,check_overlap = T) +
  # stat_ellipse(aes(x = NMDS1, y = NMDS2, colour = Code),show.legend=T) +
  geom_mark_ellipse(expand = 0,aes(fill=Code))+
  ggtitle("NMDS its2 966 only ") +
  theme_classic()
#ggsave("bc_all.pdf")


#981 ####
DIV_RelA_stats_981<-subset_samples(coralDIV2.prune_stats, TagID=="981")
  DIV_RelA_stats_981 = prune_taxa(taxa_sums(DIV_RelA_stats_981) > 0, DIV_RelA_stats_981) #this removes any OTU with 0s

#all speices
set.seed(30)

#make bray curtis data matrix
bc.981 <- phyloseq::distance(coralDIV2.prune_stats, method = "bray")
  samp.df_981 <- as(sample_data(coralDIV2.prune_stats), "data.frame") #sample df
#adonis test
adonis(bc.981 ~ SampLoc, data = samp.df_981)


#Ordination NMDS for all species
set.seed(30)
ord.DIV_RelA_stats.981 <- ordinate(DIV_RelA_stats_981, "NMDS", "bray", trymax = 100) 
stressplot(ord.DIV_RelA_stats.981)
  samp.df_981 <- as(sample_data(DIV_RelA_stats_981), "data.frame") #sample df

ord.DIV_RelA_stats.981 <- as.data.frame(cbind(vegan::scores(ord.DIV_RelA_stats.981, display="sites"))) #make df
ord.DIV_RelA_stats.981$SampLoc <- samp.df_981$SampLoc
ord.DIV_RelA_stats.981$sample_name <- samp.df_981$sample_name
ord.DIV_RelA_stats.981$Location <- samp.df_981$Location

ggplot(ord.DIV_RelA_stats.981, aes(x = NMDS1, y = NMDS2)) + 
  geom_point(aes(colour = Location, shape=Location), size = 4) +
  #scale_color_manual(values=Mcap.Parent.colors)+
  #geom_text(label = rownames(scores), nudge_x = 0.05, nudge_y = 0.05,check_overlap = T) +
  ggtitle("NMDS its2 Bray Curtis 981") +
  theme_classic() 
#ggsave("bc_all.pdf")

ggplot(ord.DIV_RelA_stats.981, aes(x = NMDS1, y = NMDS2)) + 
  geom_point(aes(colour = Location), size = 4,show.legend=T) +
  #scale_Dolor_manual(values=Sp.Dolors)+
  # geom_text(label = rownames(Clade), nudge_x = 0.05, nudge_y = 0.05,check_overlap = T) +
  # stat_ellipse(aes(x = NMDS1, y = NMDS2, colour = Code),show.legend=T) +
  # geom_mark_ellipse(expand = 0,aes(fill=Location))+
    geom_mark_hull(expand = 0,aes(fill=Location))+

  ggtitle("NMDS its2 981 only ") +
  theme_classic()
#ggsave("bc_all.pdf")


#957 ####
DIV_RelA_stats_957<-subset_samples(coralDIV2.prune_stats, TagID=="957")
  DIV_RelA_stats_957 = prune_taxa(taxa_sums(DIV_RelA_stats_957) > 0, DIV_RelA_stats_957) #this removes any OTU with 0s

#all speices
set.seed(30)

#make bray curtis data matrix
bc.957 <- phyloseq::distance(coralDIV2.prune_stats, method = "bray")
  samp.df_957 <- as(sample_data(coralDIV2.prune_stats), "data.frame") #sample df
#adonis test
adonis(bc.957 ~ SampLoc, data = samp.df_957)


#Ordination NMDS for all species
set.seed(30)
ord.DIV_RelA_stats.957 <- ordinate(DIV_RelA_stats_957, "NMDS", "bray", trymax = 100) 
stressplot(ord.DIV_RelA_stats.957)
  samp.df_957 <- as(sample_data(DIV_RelA_stats_957), "data.frame") #sample df

ord.DIV_RelA_stats.957 <- as.data.frame(cbind(vegan::scores(ord.DIV_RelA_stats.957, display="sites"))) #make df
ord.DIV_RelA_stats.957$SampLoc <- samp.df_957$SampLoc
ord.DIV_RelA_stats.957$sample_name <- samp.df_957$sample_name
ord.DIV_RelA_stats.957$Location <- samp.df_957$Location

ggplot(ord.DIV_RelA_stats.957, aes(x = NMDS1, y = NMDS2)) + 
  geom_point(aes(colour = Location), size = 7) +
  #scale_color_manual(values=Mcap.Parent.colors)+
  #geom_text(label = rownames(scores), nudge_x = 0.05, nudge_y = 0.05,check_overlap = T) +
  ggtitle("NMDS its2 Bray Curtis 957") +
  theme_classic() 
#ggsave("bc_all.pdf")

ggplot(ord.DIV_RelA_stats.957, aes(x = NMDS1, y = NMDS2)) + 
  geom_point(aes(colour = Location), size = 4,show.legend=T) +
  #scale_Dolor_manual(values=Sp.Dolors)+
  # geom_text(label = rownames(Clade), nudge_x = 0.05, nudge_y = 0.05,check_overlap = T) +
  # stat_ellipse(aes(x = NMDS1, y = NMDS2, colour = Code),show.legend=T) +
  # geom_mark_ellipse(expand = 0,aes(fill=Location))+
    geom_mark_hull(expand = 0,aes(fill=Location))+

  ggtitle("NMDS its2 957 only ") +
  theme_classic()
#ggsave("bc_all.pdf")




#985 ####
DIV_RelA_stats_985<-subset_samples(coralDIV2.prune_stats, TagID=="985")
  DIV_RelA_stats_985 = prune_taxa(taxa_sums(DIV_RelA_stats_985) > 0, DIV_RelA_stats_985) #this removes any OTU with 0s

#all speices
set.seed(30)

#make bray curtis data matrix
bc.985 <- phyloseq::distance(coralDIV2.prune_stats, method = "bray")
  samp.df_985 <- as(sample_data(coralDIV2.prune_stats), "data.frame") #sample df
#adonis test
adonis(bc.985 ~ SampLoc, data = samp.df_985)


#Ordination NMDS for all species
set.seed(30)
ord.DIV_RelA_stats.985 <- ordinate(DIV_RelA_stats_985, "NMDS", "bray", trymax = 100) 
stressplot(ord.DIV_RelA_stats.985)
  samp.df_985 <- as(sample_data(DIV_RelA_stats_985), "data.frame") #sample df

ord.DIV_RelA_stats.985 <- as.data.frame(cbind(vegan::scores(ord.DIV_RelA_stats.985, display="sites"))) #make df
ord.DIV_RelA_stats.985$SampLoc <- samp.df_985$SampLoc
ord.DIV_RelA_stats.985$sample_name <- samp.df_985$sample_name
ord.DIV_RelA_stats.985$Location <- samp.df_985$Location

ggplot(ord.DIV_RelA_stats.985, aes(x = NMDS1, y = NMDS2)) + 
  geom_point(aes(colour = Location), size = 7) +
  #scale_color_manual(values=Mcap.Parent.colors)+
  #geom_text(label = rownames(scores), nudge_x = 0.05, nudge_y = 0.05,check_overlap = T) +
  ggtitle("NMDS its2 Bray Curtis 985") +
  theme_classic() 
#ggsave("bc_all.pdf")

ggplot(ord.DIV_RelA_stats.985, aes(x = NMDS1, y = NMDS2)) + 
  geom_point(aes(colour = Location), size = 4,show.legend=T) +
  #scale_Dolor_manual(values=Sp.Dolors)+
  # geom_text(label = rownames(Clade), nudge_x = 0.05, nudge_y = 0.05,check_overlap = T) +
  # stat_ellipse(aes(x = NMDS1, y = NMDS2, colour = Code),show.legend=T) +
  geom_mark_hull(expand = 0,aes(fill=Location))+
  ggtitle("NMDS its2 985 only ") +
  theme_classic()
#ggsave("bc_all.pdf")


#959 ####
DIV_RelA_stats_959<-subset_samples(coralDIV2.prune_stats, TagID=="959")
  DIV_RelA_stats_959 = prune_taxa(taxa_sums(DIV_RelA_stats_959) > 0, DIV_RelA_stats_959) #this removes any OTU with 0s

#all speices
set.seed(30)

#make bray curtis data matrix
bc.959 <- phyloseq::distance(coralDIV2.prune_stats, method = "bray")
  samp.df_959 <- as(sample_data(coralDIV2.prune_stats), "data.frame") #sample df
#adonis test
adonis(bc.959 ~ SampLoc, data = samp.df_959)


#Ordination NMDS for all species
set.seed(30)
ord.DIV_RelA_stats.959 <- ordinate(DIV_RelA_stats_959, "NMDS", "bray", trymax = 100) 
stressplot(ord.DIV_RelA_stats.959)
  samp.df_959 <- as(sample_data(DIV_RelA_stats_959), "data.frame") #sample df

ord.DIV_RelA_stats.959 <- as.data.frame(cbind(vegan::scores(ord.DIV_RelA_stats.959, display="sites"))) #make df
ord.DIV_RelA_stats.959$SampLoc <- samp.df_959$SampLoc
ord.DIV_RelA_stats.959$sample_name <- samp.df_959$sample_name
ord.DIV_RelA_stats.959$Sub.loc <- samp.df_959$Sub.loc
ord.DIV_RelA_stats.959$Code<-paste(ord.DIV_RelA_stats.959$SampLoc,ord.DIV_RelA_stats.959$Sub.loc)

ggplot(ord.DIV_RelA_stats.959, aes(x = NMDS1, y = NMDS2)) + 
  geom_point(aes(colour = Code), size = 7) +
  #scale_color_manual(values=Mcap.Parent.colors)+
  #geom_text(label = rownames(scores), nudge_x = 0.05, nudge_y = 0.05,check_overlap = T) +
  ggtitle("NMDS its2 Bray Curtis 959") +
  theme_classic() 
#ggsave("bc_all.pdf")

ggplot(ord.DIV_RelA_stats.959, aes(x = NMDS1, y = NMDS2)) + 
  geom_point(aes(colour = Sub.loc), size = 4,show.legend=T) +
  #scale_Dolor_manual(values=Sp.Dolors)+
  # geom_text(label = rownames(Clade), nudge_x = 0.05, nudge_y = 0.05,check_overlap = T) +
  # stat_ellipse(aes(x = NMDS1, y = NMDS2, colour = Code),show.legend=T) +
  geom_mark_hull(expand = 0,aes(fill=Sub.loc))+
  ggtitle("NMDS its2 959 only ") +
  theme_classic()
#ggsave("bc_all.pdf")


#961 ####
DIV_RelA_stats_961<-subset_samples(coralDIV2.prune_stats, TagID=="961")
  DIV_RelA_stats_961 = prune_taxa(taxa_sums(DIV_RelA_stats_961) > 0, DIV_RelA_stats_961) #this removes any OTU with 0s

#all speices
set.seed(30)

#make bray curtis data matrix
bc.961 <- phyloseq::distance(coralDIV2.prune_stats, method = "bray")
  samp.df_961 <- as(sample_data(coralDIV2.prune_stats), "data.frame") #sample df
#adonis test
adonis(bc.961 ~ SampLoc, data = samp.df_961)


#Ordination NMDS for all species
set.seed(30)
ord.DIV_RelA_stats.961 <- ordinate(DIV_RelA_stats_961, "NMDS", "bray", trymax = 100) 
stressplot(ord.DIV_RelA_stats.961)
  samp.df_961 <- as(sample_data(DIV_RelA_stats_961), "data.frame") #sample df

ord.DIV_RelA_stats.961 <- as.data.frame(cbind(vegan::scores(ord.DIV_RelA_stats.961, display="sites"))) #make df
ord.DIV_RelA_stats.961$SampLoc <- samp.df_961$SampLoc
ord.DIV_RelA_stats.961$sample_name <- samp.df_961$sample_name
ord.DIV_RelA_stats.961$Sub.loc <- samp.df_961$Sub.loc
ord.DIV_RelA_stats.961$Code<-paste(ord.DIV_RelA_stats.961$SampLoc,ord.DIV_RelA_stats.961$Sub.loc)

ggplot(ord.DIV_RelA_stats.961, aes(x = NMDS1, y = NMDS2)) + 
  geom_point(aes(colour = Code), size = 7) +
  #scale_color_manual(values=Mcap.Parent.colors)+
  #geom_text(label = rownames(scores), nudge_x = 0.05, nudge_y = 0.05,check_overlap = T) +
  ggtitle("NMDS its2 Bray Curtis 961") +
  theme_classic() 
#ggsave("bc_all.pdf")

ggplot(ord.DIV_RelA_stats.961, aes(x = NMDS1, y = NMDS2)) + 
  geom_point(aes(colour = Code), size = 4,show.legend=T) +
  #scale_Dolor_manual(values=Sp.Dolors)+
  # geom_text(label = rownames(Clade), nudge_x = 0.05, nudge_y = 0.05,check_overlap = T) +
  # stat_ellipse(aes(x = NMDS1, y = NMDS2, colour = Code),show.legend=T) +
  geom_mark_hull(expand = 0,aes(fill=Code))+
  ggtitle("NMDS its2 961 only ") +
  theme_classic()
#ggsave("bc_all.pdf")




######### Try by tips and bases only #### 
coralDIV2.prune_statsBranch<-subset_samples(coralDIV2.prune_stats, SampLoc=="Branch")
coralDIV2.prune_statsBranch = prune_taxa(taxa_sums(coralDIV2.prune_statsBranch) > 0, coralDIV2.prune_statsBranch)
  
set.seed(10)
ord.DIV_bc.Branch <- ordinate(coralDIV2.prune_statsBranch, "NMDS", "bray", trymax = 500)  ### NO CONVERGENCE
stressplot(ord.DIV_bc.Branch)
  samp.df.Branch <- as(sample_data(coralDIV2.prune_statsBranch), "data.frame") #sample df

ord.DIV_bc.Branch <- as.data.frame(cbind(vegan::scores(ord.DIV_bc.Branch, display="sites"))) #make df
ord.DIV_bc.Branch$TagID <- samp.df.Branch$TagID
ord.DIV_bc.Branch$TagID<-as.factor(ord.DIV_bc.Branch$TagID)
ord.DIV_bc.Branch$SampLoc <- samp.df.Branch$SampLoc
ord.DIV_bc.Branch$Location<-samp.df.Branch$Sub.loc
ord.DIV_bc.Branch$Code<-paste(ord.DIV_bc.Branch$SampLoc, ord.DIV_bc.Branch$Location)
ord.DIV_bc.Branch$Code<-as.factor(ord.DIV_bc.Branch$Code)

ggplot(ord.DIV_bc.Branch, aes(x = NMDS1, y = NMDS2)) + 
  geom_point(aes(colour = TagID), size = 4,show.legend=T) +
  #scaleBrancholor_manual(values=Sp.Brancholors)+
  # geom_text(label = rownames(Clade), nudge_x = 0.05, nudge_y = 0.05,check_overlap = T) +
  stat_ellipse(aes(x = NMDS1, y = NMDS2, colour = TagID),show.legend=T) +
  ggtitle("NMDS its2 C only ") +
  themeBranchlassic()
#ggsave("bc_all.pdf")
```


